---
title: "Kākāpō chick and nest fungal biota analyses"
author: "Annie G. West"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages into session, and print package version.

```{r results='hide'}
library(ggplot2); packageVersion("ggplot2")
library(phyloseq); packageVersion("phyloseq")
library(gridExtra); packageVersion("gridExtra")
library(ggsignif); packageVersion("ggsignif")
library(ggrepel); packageVersion("ggrepel")
library(ggsci); packageVersion("ggsci")
library(hrbrthemes); packageVersion("hrbrthemes")
library(tidyverse); packageVersion("tidyverse")
library(viridis); packageVersion("viridis")
library(dplyr); packageVersion("dplyr")
library(extrafont); packageVersion("extrafont")
library(data.table); packageVersion("data.table")

set.seed(100)
```

##Import data

```{r}
ASV_table <- fread("output/ITS_ASV_table_nochim.txt")
ASV_table <- data.frame(ASV_table, row.names = 1)

to.delete <- c("FHMNA-05-5","FZENA-04-3","FKU3B-13-5","F-KUP-13-5")
ASV_table <- ASV_table[!(rownames(ASV_table) %in% to.delete),]


OTU <- otu_table(ASV_table, taxa_are_rows = F) 
sum(rowSums(OTU)) #2044346
```


```{r}
taxa <- read.table("output/ITS_taxa_table.txt")
taxa$Family[is.na(taxa$Family)]="Unclassified"
taxa$Genus[is.na(taxa$Genus)]="Unclassified"
taxa$Species[is.na(taxa$Species)]="unclassified"
taxa$Taxonomy <- paste(taxa$Genus, taxa$Species, sep=" ")

taxmatrix <- as.matrix(taxa) #make sure its a matrix
TAX <- tax_table(taxmatrix) # create a phyloseq TAXA table
```


```{r}
map <- read.table("ITS_nest_chick_map.txt",header = TRUE, sep = '\t')
rownames(map) <- map$SAMPLEID
map <- sample_data(map)


setdiff(rownames(OTU), rownames(map))
rownames(OTU)[rownames(OTU) == "FKUNB10-4"] <- "FKUNB-10-4"
rownames(map) == rownames(OTU)
map <- map[rownames(OTU),]
identical(rownames(OTU), rownames(map))


map$Nest <- factor(map$Nest, 
                   levels = c("ALICE_NA","ARANGA_NB","ATARETA_NA","CYNDY_NB","ESPERANCE_NB","FOLLOW_UP",
                              "HAND_REARING","HOKI_NA","HUHANA_NA","IHI_NB","KUIHI_NB","MARAMA_NA",
                              "MARGARETMAREE_NB","NORA_NB","POUNAMU_NA","QUEENIE_NA","RAKIURA_NA","SUE_NB",
                              "TUMEKE_NB","WEHEPO_NB"),
                    labels = c("Alice","Aranga","Atareta","Cyndy","Esperance","Sub-adult samples",
                              "Hand rearing","Hoki","Huhana","Ihi","Kuihi","Marama","Margaret-Maree",
                              "Nora","Pounamu","Queenie","Rakiura","Sue","Tumeke","Weheruatanga-o-te-po"))

map$NestFaeces <- factor(map$NestFaeces,
                        levels = c("LEFT","REMOVED","MIXED"),
                         labels = c("Faeces in","Faeces removed","Mixed"))

map$Aspergillosis <- factor(map$Aspergillosis,
                            levels = c("CONTROL","LINKED","YES"),
                            labels = c("Unaffected","Linked","Infected"))

map$Nest_type <- factor(map$Nest_type,
                        levels = c("A-FRAME","HAND_REARING","OPEN","HOLE","ROCK","TREE","FOLLOW_UP"),
                        labels = c("A-frame","Hand rearing","Open","Hole","Rock","Tree","Sub-adult samples"))
```

#Phyloseq
Create a phyloseq object for downstream analyses:

```{r}
ps <- phyloseq(TAX, map,
               OTU) 
ps               
ps = subset_samples(ps, SAMPLEID != "FHHNA-07-3" & SAMPLEID != "FHNA-07-3D" & SAMPLEID != "FB3A-20-2D" & SAMPLEID != "FHI2A-21-2")
ps

psF = subset_samples(ps, Type != "NEST")
psF

psN = subset_samples(ps, Type != "FAECAL")
psN
```


##Filtering with phyloseq

####Taxonomic filtering 

Use to filter out non-target taxa e.g. mitochondria etc. 
```{r}
# Show available ranks in the dataset
rank_names(ps)

ps_tax_table <- as.data.frame(tax_table(ps))
sum(is.na(ps_tax_table$Phylum)) #85 counts of 2137 taxa = 3.97% >> 2044346 reads spanning 2137 fungi taxa
str(ps_tax_table$Phylum)
sapply(ps_tax_table, n_distinct)
levels(factor(ps_tax_table$Kingdom))

plyr::count(ps_tax_table$Kingdom) #2137
```

```{r}
ps_tax_table[is.na(ps_tax_table)]="Unclassified"
asv_table_ps<-as.data.frame(t(otu_table(ps)))
asv_table_wTax_ps <- cbind(asv_table_ps, ps_tax_table)

Phyla.sum.ps<-aggregate(asv_table_wTax_ps[,1:177], list(asv_table_wTax_ps$Phylum),sum)
row.names(Phyla.sum.ps)<- Phyla.sum.ps$Group.1
Phyla.sum.ps$Group.1 <- NULL
sum(rowSums(Phyla.sum.ps)) #2040662
rowSums(Phyla.sum.ps != 0) 
P_rowsum.ps <- rowSums(Phyla.sum.ps) 

dir.create("FINAL")
dir.create("FINAL/tables")
write.csv(P_rowsum.ps, "FINAL/tables/fungi_P_rowsum_ps.csv")

genus.sum.ps<-aggregate(asv_table_wTax_ps[,1:177], list(asv_table_wTax_ps$Genus),sum)
row.names(genus.sum.ps)<- genus.sum.ps$Group.1
genus.sum.ps$Group.1 <- NULL
sum(rowSums(genus.sum.ps)) 


G_rowsum.ps <- rowSums(genus.sum.ps)
write.csv(G_rowsum.ps, "FINAL/tables/G_rowsum_ps.csv")
write.csv(genus.sum.ps, "FINAL/tables/genus_sums_ps.csv")

#1300 / 19117949 = 0.007% of reads unassigned at phylum level
```

```{r}
# Create table, number of features for each phyla
table(tax_table(ps)[, "Phylum"], exclude = NULL)

ps0 <- subset_taxa(ps, !is.na(Phylum) & !Phylum %in% c("", "uncharacterized"))

phyla2Filter = c("<NA>")
ps1 = subset_taxa(ps0, !Phylum %in% phyla2Filter) #4% NA (85/2137)

table(tax_table(ps1)[,"Phylum"], exclude = NULL)



# Show available ranks in the dataset
rank_names(psF)

# Create table, number of features for each phyla
table(tax_table(psF)[, "Phylum"], exclude = NULL)

psF0 <- subset_taxa(psF, !is.na(Phylum) & !Phylum %in% c("", "uncharacterized"))

phyla2Filter = c("<NA>")
psF1 = subset_taxa(psF0, !Phylum %in% phyla2Filter)

table(tax_table(psF1)[,"Phylum"], exclude = NULL) #4% not assigned



# Show available ranks in the dataset
rank_names(psN)

# Create table, number of features for each phyla
table(tax_table(psN)[, "Phylum"], exclude = NULL)

psN0 <- subset_taxa(psN, !is.na(Phylum) & !Phylum %in% c("", "uncharacterized"))

phyla2Filter = c("<NA>")
psN1 = subset_taxa(psN0, !Phylum %in% phyla2Filter)

table(tax_table(psN1)[,"Phylum"], exclude = NULL) #4% not assigned
```


####Filter low-abundance ASVs


```{r}
# Transform to relative abundance

# This code keeps raw read counts in the phyloseq object but filters out based on taxa row sums using relative abundance (x/sum(x))
minTotRelAbun = 1e-5

x = taxa_sums(ps1)
keepTaxa = (x / sum(x)) > minTotRelAbun  
ps2 = prune_taxa(keepTaxa, ps1)
ps2
# Save the new taxa table if you are rarefying
Ntaxa <- tax_table(ps2)


x = taxa_sums(psF1)
keepTaxa = (x / sum(x)) > minTotRelAbun  
psF2 = prune_taxa(keepTaxa, psF1)
psF2
NtaxaF <- tax_table(psF2)



x = taxa_sums(psN1)
keepTaxa = (x / sum(x)) > minTotRelAbun  
psN2 = prune_taxa(keepTaxa, psN1)
psN2
NtaxaN <- tax_table(psN2)
```

#SRS

```{r}
set.seed(100)
library(SRS)
##Samples should be arranged columnwise
#SRS.shiny.app(srs.otuF)
srs.otuF = data.frame(t(otu_table(psF2)))

#SRS.shiny.app(srs.otuN)
srs.otuN = data.frame(t(otu_table(psN2)))
```

```{r, fig.height=8, fig.width=20}
library(ggplotify)

kakapo_colours <- c("#4b5e1e", "#7D9D33", "#DCC949", "#BCA888", "#CD8862", "#775B24")

F.curve.plot <- as.ggplot(function() SRScurve(srs.otuF, metric = "richness", step = 100, max.sample.size = 2000,
          ylab = "Richness", xlab = "Faecal samples", col = "#4b5e1e", cex.lab = 1.5)  ) 

N.curve.plot <- as.ggplot(function() SRScurve(srs.otuN, metric = "richness", step = 100, max.sample.size = 3000,
          ylab = "Richness", xlab = "Litter samples", col = "#DCC949", cex.lab = 1.5)  )


curve.plots.combined = ggarrange(F.curve.plot, N.curve.plot, labels = c("A","B"), font.label = list(size = 30), 
          ncol=2, nrow=1)
curve.plots.combined.title = annotate_figure(curve.plots.combined, top = text_grob("Sub-sampling curves for ITS amplicon sequence data", face = "bold", family = "sans", size = 30))
curve.plots.combined.title

ggsave("SRS.ITS.curve.plots.combined.png", curve.plots.combined.title, width = 20, height = 8, dpi = 400, bg = "white")
```


```{r}
set.seed(100)
library(SRS)
##Samples should be arranged columnwise
###Faecal###
SRS_outputF <- SRS(srs.otuF, Cmin = 500) #14 samples discarded
SRS_outputF.df = data.frame(t(SRS_outputF))

colnames(SRS_outputF.df) = row.names(srs.otuF)
SRS_outputF.df = SRS_outputF.df[,order(colSums(SRS_outputF.df),decreasing = T)]
NtaxaF.df = as.data.frame(NtaxaF)
to.remove <- setdiff(rownames(NtaxaF.df), colnames(SRS_outputF.df))
NtaxaF.df = NtaxaF.df[!row.names(NtaxaF.df) %in% to.remove,]
setdiff(rownames(NtaxaF.df), colnames(SRS_outputF.df))
identical(rownames(NtaxaF.df), colnames(SRS_outputF.df))
NtaxaF.df = NtaxaF.df[colnames(SRS_outputF.df),]
identical(rownames(NtaxaF.df), colnames(SRS_outputF.df))
NtaxaF.df$ASV_ID <- paste("ASV_", 1:nrow(NtaxaF.df), sep="")
NtaxaF.df$concat = paste(NtaxaF.df$ASV_ID, NtaxaF.df$Taxonomy, sep = "_")
rownames(NtaxaF.df) = NtaxaF.df$concat
colnames(SRS_outputF.df) = rownames(NtaxaF.df)
NtaxaF.df$ASV_ID = NULL
NtaxaF.df$concat = NULL
NtaxaF.df = as.matrix(NtaxaF.df)


rownames(SRS_outputF.df) <- gsub(x = rownames(SRS_outputF.df), pattern = "\\.", replacement = "-") 


###Nest###
SRS_outputN <- SRS(srs.otuN, Cmin = 1600) #4 samples discarded
SRS_outputN.df = data.frame(t(SRS_outputN))

colnames(SRS_outputN.df) = row.names(srs.otuN)
SRS_outputN.df = SRS_outputN.df[,order(colSums(SRS_outputN.df),decreasing = T)]
NtaxaN.df = as.data.frame(NtaxaN)
to.remove <- setdiff(rownames(NtaxaN.df), colnames(SRS_outputN.df))
NtaxaN.df = NtaxaN.df[!row.names(NtaxaN.df) %in% to.remove,]
setdiff(rownames(NtaxaN.df), colnames(SRS_outputN.df))
identical(rownames(NtaxaN.df), colnames(SRS_outputN.df))
NtaxaN.df = NtaxaN.df[colnames(SRS_outputN.df),]
identical(rownames(NtaxaN.df), colnames(SRS_outputN.df))
NtaxaN.df$ASV_ID <- paste("ASV_", 1:nrow(NtaxaN.df), sep="")
NtaxaN.df$concat = paste(NtaxaN.df$ASV_ID, NtaxaN.df$Taxonomy, sep = "_")
rownames(NtaxaN.df) = NtaxaN.df$concat
colnames(SRS_outputN.df) = rownames(NtaxaN.df)
NtaxaN.df$ASV_ID = NULL
NtaxaN.df$concat = NULL
NtaxaN.df = as.matrix(NtaxaN.df)


rownames(SRS_outputN.df) <- gsub(x = rownames(SRS_outputN.df), pattern = "\\.", replacement = "-")
```

```{r}
write.csv(SRS_output.df, "FINAL/tables/fungi_SRS_asv_table.csv")
write.csv(SRS_outputF.df, "FINAL/tables/fungi_SRS_asv_table_F.csv")
write.csv(SRS_outputN.df, "FINAL/tables/fungi_SRS_asv_table_N.csv")
```

```{r}
map.ps2.F <- data.frame(sample_data(psF2))
f.to.delete <- setdiff(rownames(map.ps2.F), rownames(SRS_outputF.df))
map.ps2.F = map.ps2.F[!row.names(map.ps2.F) %in% f.to.delete,]
map.ps2.F$Date <- as.Date(map.ps2.F$Date, format = "%d/%m/%Y")
map.ps2.F.sort <- dplyr::arrange(map.ps2.F, Name, Date)
SRS_outputF.df.sort <- SRS_outputF.df[map.ps2.F.sort$SAMPLEID,]

psF_SRS = phyloseq(otu_table(SRS_outputF.df.sort, taxa_are_rows = F), 
                sample_data(map.ps2.F.sort),
                tax_table(NtaxaF.df))

psF_SRS      #1303  taxa by 108 samples
psF_SRS_otu = data.frame(otu_table(psF_SRS))
avg_ASV_F <- data.frame(rowSums(psF_SRS_otu != 0))
# 3 to 136 mean = 30
prev_ASV_F <- data.frame(colSums(psF_SRS_otu != 0))
#ASV_1_Kazachstania.telluris    96
#ASV_2_Debaryomyces.hansenii    94
#ASV_3_Apiotrichum.unclassified 93


sample_data(psF_SRS)$Age <- factor(sample_data(psF_SRS)$Age, 
                                         levels = c("<20 days","20--40 days","40--60 days","60--80 days","200+ days"),
                                         labels = c("<20 days","20 - 40 days","40 - 60 days","60 - 80 days","200+ days"))


map.ps2.N <- data.frame(sample_data(psN2))
n.to.delete <- setdiff(rownames(map.ps2.N), rownames(SRS_outputN.df))
map.ps2.N = map.ps2.N[!row.names(map.ps2.N) %in% n.to.delete,]
map.ps2.N$Date <- as.Date(map.ps2.N$Date, format = "%d/%m/%Y")
map.ps2.N.sort <- dplyr::arrange(map.ps2.N, Name, Date)
SRS_outputN.df.sort <- SRS_outputN.df[map.ps2.N.sort$SAMPLEID,]

psN_SRS = phyloseq(otu_table(SRS_outputN.df.sort, taxa_are_rows = F), 
                sample_data(map.ps2.N.sort),
                tax_table(NtaxaN.df))

psN_SRS      #1008 taxa by 51 samples
psN_SRS_otu = data.frame(otu_table(psN_SRS))
avg_ASV_N <- data.frame(rowSums(psN_SRS_otu != 0))
# 2 to 175 mean = 68
prev_ASV_N <- data.frame(colSums(psN_SRS_otu != 0))
#ASV_2_Apiotrichum.unclassified   51
#ASV_1_Debaryomyces.hansenii      49
#ASV_6_Apiotrichum.unclassified   39

sample_data(psN_SRS)$Name <- factor(sample_data(psN_SRS)$Name, 
                                          levels = c("ALICE_NEST","ARANGA_NEST","CYNDY_NEST","ESPERANCE_NEST",
                                                     "HOKI_NEST","HUHANA_NEST","IHI_NEST","KUIHI_NEST","MARAMA_NEST",
                                                     "MARGARETMAREE_NEST","NORA_NEST","POUNAMU_NEST","RAKIURA_NEST","SUE_NEST",
                                                     "WEHEPO_NEST"),
                                          labels = c("Alice","Aranga","Cyndy","Esperance","Hoki","Huhana","Ihi","Kuihi",
                                                    "Marama","Margaret-Maree","Nora","Pounamu","Rakiura","Sue","Weheruatanga-o-te-po"))

sample_data(psN_SRS)$Age <- factor(sample_data(psN_SRS)$Age, 
                                         levels = c("<20 days","20--40 days","40--60 days","60--90 days"),
                                         labels = c("<20 days","20 - 40 days","40 - 60 days","60 - 90 days"))
```
#Data summaries
```{r}
library(dplyr); packageVersion("dplyr")
map.f <- data.frame(sample_data(psF_SRS))
map.n <- data.frame(sample_data(psN_SRS))

pool = c("POOL")
map.f.np = map.f[!(map.f$Group %in% pool),]

summary_data <- map.f.np %>%
    group_by(Nest_type, Name) %>%
    dplyr::summarise(Count = n()) 
summary_data

map.f %>% count(Group)
map.f.np %>% count(Name)
map.f %>% count(Age)
map.f %>% count(Aspergillosis)
map.f %>% count(Nest)
map.f %>% count(Nest_type)
map.f %>% count(NestFaeces)
map.f %>% count(Island)
map.f %>% count(Movement)

map.n %>% count(Age)
map.n %>% count(Aspergillosis)
map.n %>% count(Nest)
map.n %>% count(Nest_type)
map.n %>% count(NestFaeces)
map.n %>% count(Island)
map.n %>% count(Movement)
```

```{r}
SRS_asv_tableF<-as.data.frame(t(otu_table(psF_SRS)))
SRS_taxo_tableF<-as.data.frame(tax_table(psF_SRS))
SRS_asv_table_wTaxF <- cbind(SRS_asv_tableF, SRS_taxo_tableF)

SRS_asv_tableN<-as.data.frame(t(otu_table(psN_SRS)))
SRS_taxo_tableN<-as.data.frame(tax_table(psN_SRS))
SRS_asv_table_wTaxN <- cbind(SRS_asv_tableN, SRS_taxo_tableN)
```

```{r}
#Phylum
Phyla.sumF<-aggregate(SRS_asv_table_wTaxF[,1:108], list(SRS_asv_table_wTaxF$Phylum),sum)
row.names(Phyla.sumF)<- Phyla.sumF$Group.1
Phyla.sumF$Group.1 <- NULL
P_rowsumF <- rowSums(Phyla.sumF)
write.csv(Phyla.sumF, "FINAL/tables/fungi_Phyla_sumF_per_sample_NC_kakapo.csv")
write.csv(P_rowsumF, "FINAL/tables/fungi_P_rowsumF_NC_kakapo_fungi.csv")


Phyla.sumN<-aggregate(SRS_asv_table_wTaxN[,1:51], list(SRS_asv_table_wTaxN$Phylum),sum)
row.names(Phyla.sumN)<- Phyla.sumN$Group.1
Phyla.sumN$Group.1 <- NULL
P_rowsumN <- rowSums(Phyla.sumN)
write.csv(Phyla.sumN, "FINAL/tables/fungi_Phyla_sumN_per_sample_NC_kakapo.csv")
write.csv(P_rowsumN, "FINAL/tables/fungi_P_rowsumN_NC_kakapo.csv")


sum(rowSums(Phyla.sumF)) #54000
rowSums(Phyla.sumF != 0)

sum(rowSums(Phyla.sumN)) #81600
rowSums(Phyla.sumN != 0)
```

```{r}
Class.sumF <- aggregate(SRS_asv_table_wTaxF[,1:108], list(SRS_asv_table_wTaxF$Class),sum)
row.names(Class.sumF)<- Class.sumF$Group.1
Class.sumF$Group.1 <- NULL
C_rowsumF <- rowSums(Class.sumF) 
write.csv(C_rowsumF, "FINAL/tables/fungi_class_rowsumF_NC_kakapo.csv")
write.csv(Class.sumF, "FINAL/tables/fungi_Class_sumF_per_sample_NC_kakapo.csv")

Class.sumN <- aggregate(SRS_asv_table_wTaxN[,1:51], list(SRS_asv_table_wTaxN$Class),sum)
row.names(Class.sumN)<- Class.sumN$Group.1
Class.sumN$Group.1 <- NULL
C_rowsumN <- rowSums(Class.sumN) 
write.csv(C_rowsumN, "FINAL/tables/fungi_class_rowsumN_NC_kakapo.csv")
write.csv(Class.sumN, "FINAL/tables/fungi_class_sumN_per_sample_NC_kakapo.csv")
```


```{r}
Genus.sumF <- aggregate(SRS_asv_table_wTaxF[,1:108], list(SRS_asv_table_wTaxF$Genus),sum)
row.names(Genus.sumF)<- Genus.sumF$Group.1
Genus.sumF$Group.1 <- NULL
G_rowsumF <- rowSums(Genus.sumF) 
write.csv(G_rowsumF, "FINAL/tables/fungi_genus_rowsumF_NC_kakapo.csv")
write.csv(Genus.sumF, "FINAL/tables/fungi_Genus_sumF_per_sample_NC_kakapo.csv")

Genus.sumN <- aggregate(SRS_asv_table_wTaxN[,1:51], list(SRS_asv_table_wTaxN$Genus),sum)
row.names(Genus.sumN)<- Genus.sumN$Group.1
Genus.sumN$Group.1 <- NULL
G_rowsumN <- rowSums(Genus.sumN) 
write.csv(G_rowsumN, "FINAL/tables/fungi_genus_rowsumN_NC_kakapo.csv")
write.csv(Genus.sumN, "FINAL/tables/fungi_Genus_sumN_per_sample_NC_kakapo.csv")
```

```{r}
taxa.sumF <- aggregate(SRS_asv_table_wTaxF[,1:108], list(SRS_asv_table_wTaxF$Taxonomy),sum)
row.names(taxa.sumF)<- taxa.sumF$Group.1
taxa.sumF$Group.1 <- NULL
t_rowsumF <- rowSums(taxa.sumF) 
write.csv(t_rowsumF, "FINAL/tables/fungi_taxa_rowsumF_NC_kakapo.csv")
write.csv(taxa.sumF, "FINAL/tables/fungi_taxa_sumF_per_sample_NC_kakapo.csv")

taxa.sumN <- aggregate(SRS_asv_table_wTaxN[,1:51], list(SRS_asv_table_wTaxN$Taxonomy),sum)
row.names(taxa.sumN)<- taxa.sumN$Group.1
taxa.sumN$Group.1 <- NULL
t_rowsumN <- rowSums(taxa.sumN) 
write.csv(t_rowsumN, "FINAL/tables/fungi_taxa_rowsumN_NC_kakapo.csv")
write.csv(taxa.sumN, "FINAL/tables/fungi_taxa_sumN_per_sample_NC_kakapo.csv")
```

#PERMANOVA
###Poo removal
```{r}
library(vegan)
set.seed(100)

#Faecal
permanova.dis.F <- distance(psF_SRS, "bray")
adonis2(permanova.dis.F ~ NestFaeces, map.f, 
        permutations = how(nperm = 9999, within=Within(type="series"), plots=Plots(strata=map.f$Name)))

beta.pooR <- vegan::betadisper(permanova.dis.F, map.f$NestFaeces)
beta.pooR
vegan::permutest(beta.pooR,permutations = how(nperm = 9999)) 


#Nest
permanova.dis.N <- phyloseq::distance(psN_SRS, "bray")
adonis2(permanova.dis.N ~ NestFaeces, map.n, 
        permutations = how(nperm = 9999, within=Within(type="series"), plots=Plots(strata=map.n$Name)))

beta.pooR.N <- vegan::betadisper(permanova.dis.N, map.n$NestFaeces)
beta.pooR.N
vegan::permutest(beta.pooR.N) 
```

###Faecal
```{r}
set.seed(100)
source('pairwiseAdonis3.R')
###FAECAL###

#Aspergillosis
vegan::adonis2(permanova.dis.F ~ Aspergillosis, map.f, 
               permutations = how(nperm = 9999, within=Within(type="series"), plots=Plots(strata=map.f$Name))) 

beta.asp <- vegan::betadisper(permanova.dis.F, map.f$Aspergillosis)
beta.asp
vegan::permutest(beta.asp, permutations = how(nperm = 9999)) 


#Movement
vegan::adonis2(permanova.dis.F ~ Movement, map.f,
               permutations = how(nperm = 9999, within=Within(type="series"), plots=Plots(strata=map.f$Name)))

beta.m <- vegan::betadisper(permanova.dis.F, map.f$Movement)
beta.m
vegan::permutest(beta.m, permutations = how(nperm = 9999))



#Island
psF_sub_is <- subset_samples(psF_SRS, Island != "Hand rearing") 
disF.sub.is <- distance(psF_sub_is, "bray")
mapF.sub.is <- data.frame(sample_data(psF_sub_is))
vegan::adonis2(disF.sub.is ~ Island, mapF.sub.is, 
               permutations = how(nperm = 9999, within=Within(type="series"), plots=Plots(strata=mapF.sub.is$Name)))


beta.l <- vegan::betadisper(permanova.dis.F, map.f$Island)
beta.l
vegan::permutest(beta.l, permutations = how(nperm = 9999)) 



#Age
vegan::adonis2(permanova.dis.F ~ Age, map.f, 
               permutations = how(nperm = 9999, within=Within(type="series"), plots=Plots(strata=map.f$Name)))

pairwise.adonis3(permanova.dis.F ~ Age, data = map.f, p.adjust.m = 'BH', strata = "Name", nperm = 9999, within_type = "series")

beta.age <- vegan::betadisper(permanova.dis.F, map.f$Age)
beta.age
vegan::permutest(beta.age) 



beta.age.df <- data.frame(beta.age$distances)
beta.age.df$Group = beta.age$group
dunn.test::dunn.test(beta.age.df$beta.age.distances, beta.age.df$Group, method = "bh")
                    

#Nest type
##No sub-adult samples
psF_sub_NT <- subset_samples(psF_sub_is, Nest_type != "Sub-adult samples") 
disF.sub.NT <- distance(psF_sub_NT, "bray")
mapF.sub.NT <- data.frame(sample_data(psF_sub_NT))
vegan::adonis2(disF.sub.NT ~ Nest_type, mapF.sub.NT, 
               permutations = how(nperm = 9999, within=Within(type="series"), plots=Plots(strata=mapF.sub.NT$Name)))

beta.nt <- vegan::betadisper(disF.sub.NT, mapF.sub.NT$Nest_type)
beta.nt
vegan::permutest(beta.nt, permutations = how(nperm = 9999)) 

#Nest
##No sub-adult samples
vegan::adonis2(disF.sub.NT ~ Nest, mapF.sub.NT, 
               permutations = how(nperm = 9999, within=Within(type="series"), plots=Plots(strata=mapF.sub.NT$Name)))

beta.n <- vegan::betadisper(disF.sub.NT, mapF.sub.NT$Nest)
beta.n
vegan::permutest(beta.n, permutations = how(nperm = 9999))


#Chick
vegan::adonis2(permanova.dis.F ~ Name, map.f, 
               permutations = how(nperm = 9999, within=Within(type="series"), plots=Plots(strata=map.f$Name)))

```

###Litter
```{r}
###NEST###

#Aspergillosis
vegan::adonis2(permanova.dis.N ~ Aspergillosis, map.n, 
               permutations = how(nperm = 9999, within=Within(type="series"), plots=Plots(strata=map.n$Name)))

vegan::adonis2(permanova.dis.N ~ Island + Aspergillosis, map.n, 
               permutations = how(nperm = 9999, within=Within(type="series"), plots=Plots(strata=map.n$Name)))

beta.asp.L <- vegan::betadisper(permanova.dis.N, map.n$Aspergillosis)
beta.asp.L
vegan::permutest(beta.asp.L, permutations = how(nperm = 9999))

#Movement
vegan::adonis2(permanova.dis.N ~ Movement, map.n, 
               permutations = how(nperm = 9999, within=Within(type="series"), plots=Plots(strata=map.n$Name)))

beta.M.L <- vegan::betadisper(permanova.dis.N, map.n$Movement)
beta.M.L
vegan::permutest(beta.M.L) 

#Island
vegan::adonis2(permanova.dis.N ~ Island, map.n, 
               permutations = how(nperm = 9999, within=Within(type="series"), plots=Plots(strata=map.n$Name)))

beta.I.L <- vegan::betadisper(permanova.dis.N, map.n$Island)
beta.I.L
vegan::permutest(beta.I.L) 

#Days since first chick
vegan::adonis2(permanova.dis.N ~ Age, map.n, 
               permutations = how(nperm = 9999, within=Within(type="series"), plots=Plots(strata=map.n$Name)))

pairwise.adonis3(permanova.dis.N ~ Age, data = map.n, p.adjust.m = 'BH', strata = "Name", nperm = 9999, within_type = "series")

beta.age.L <- vegan::betadisper(permanova.dis.N, map.n$Age)
beta.age.L
vegan::permutest(beta.age.L, permutations = how(nperm = 9999))

#Nest type
vegan::adonis2(permanova.dis.N ~ Nest_type, map.n, 
               permutations = how(nperm = 9999, within=Within(type="series"), plots=Plots(strata=map.n$Name)))

beta.NT.L <- vegan::betadisper(permanova.dis.N, map.n$Nest_type)
beta.NT.L
vegan::permutest(beta.NT.L, permutations = how(nperm = 9999))

#Nest
vegan::adonis2(permanova.dis.N ~ Nest, map.n, 
               permutations = how(nperm = 9999, within=Within(type="series"), plots=Plots(strata=map.n$Name)))

```

```{r}
f.per.p.adj <- c("0.5","1","1","0.33","0.00001","0.23","0.53","1")
l.per.p.adj <- c("1","1","1","1","0.04","1","1")

p.adjust(f.per.p.adj, method = "BH")
p.adjust(l.per.p.adj, method = "BH")

f.beta.p.adj <- c("0.33","0.11","0.003","0.72","0.003","0.0006")
l.beta.p.adj <- c("0.81","0.39","0.66","0.01","0.21","0.06")

p.adjust(f.beta.p.adj, method = "BH")
p.adjust(l.beta.p.adj, method = "BH")

```



#####BC boxplots

```{r}
boxplot_theme <- theme_ipsum() + theme(plot.title = element_text(size = 28),
  
          plot.subtitle = element_text(size = 26),
          
          axis.text.x = element_blank(),

          axis.title.x = element_text(size=26),

          axis.ticks.x = element_blank(),

          axis.text.y=element_text(size=20),

          axis.title.y=element_text(size=26),

          axis.line.x=element_line(color="black",size=1.0,linetype=1),

          axis.line.y=element_line(color="black",size=1.0,linetype=1),

          panel.grid.major = element_blank(),

          panel.grid.minor = element_blank(),

          panel.background = element_blank(),

          legend.box.background = element_rect(),

          legend.box.margin = margin(5, 5, 5, 5),

          legend.position="bottom",

          legend.title = element_text(face = "bold", size = 28),
          
          legend.text = element_text(size = 26))
```



```{r fig.height= 10, fig.width=12}
library(vegan)
library(reshape2)
library(pairwiseAdonis)
library(Manu)

otu_split.F <- data.frame(otu_table(psF_SRS))
rownames(otu_split.F) <- map.f$Full
otu_split.F1.BC <- split(otu_split.F, map.f$NestFaeces)

dist.list.f.bc<- c() 

for (i in 1:length(otu_split.F1.BC)) {
     dist.list.f.bc[[i]] <- as.matrix(vegdist(otu_split.F1.BC[[i]], method = "bray"))
}

names(dist.list.f.bc) = names(otu_split.F1.BC)
df.f.bc <- melt(dist.list.f.bc)
names(df.f.bc) <- c("Sample1", "Sample2", "BCdistance","Faecal_experiment")

df.f.bc$match = df.f.bc$Sample1 == df.f.bc$Sample2
df.f.bc.2 = df.f.bc[-which(df.f.bc$match == "TRUE"),]

faecal.bc.boxplot <- ggplot(df.f.bc.2,aes(x = Faecal_experiment, y = BCdistance)) + 
  geom_jitter(position = position_jitter(0.3), aes(color = Faecal_experiment), alpha = 0.75) +
  geom_boxplot(size=1.0, fill='transparent') + 
  boxplot_theme +
  guides(colour = guide_legend(override.aes = list(size=6))) +
  labs(x = "Faecal experiment", y = "Bray-Curtis dissimilarity") +
  ggtitle("Faecal samples", subtitle =  "PERMANOVA p = 0.5") +
  scale_color_manual(name = "Bray-Curtis distances",values= get_pal("Kakapo"))
faecal.bc.boxplot

kakapo_colours <- c("#4b5e1e", "#7D9D33", "#DCC949", "#BCA888", "#CD8862", "#775B24")

faecal.bc.boxplot.nojitter <- ggplot(df.f.bc.2,aes(x = Faecal_experiment, y = BCdistance)) + 
  geom_boxplot(size=1.0, aes(fill = Faecal_experiment)) + 
  boxplot_theme +
  labs(x = "Faecal experiment", y = "Bray-Curtis dissimilarity") +
  ggtitle("Faecal samples", subtitle =  "PERMANOVA p = 0.50") +
  scale_fill_manual(name = "Bray-Curtis distances",values= c("#4b5e1e", "#7D9D33", "#BCA888"))
faecal.bc.boxplot.nojitter
#ggsave("FINAL/boxplots/fungi_bc_faecal_pooR_nojitter.png", faecal.bc.boxplot.nojitter, height = 10, width = 12, dpi = 400)
```

```{r fig.height= 10, fig.width=12}
otu_split.N <- data.frame(otu_table(psN_SRS))
rownames(otu_split.N) <- map.n$Full
otu_split.N1.BC <- split(otu_split.N, map.n$NestFaeces)

dist.list.n.bc<- c() 

for (i in 1:length(otu_split.N1.BC)) {
     dist.list.n.bc[[i]] <- as.matrix(vegdist(otu_split.N1.BC[[i]], method = "bray"))
}

names(dist.list.n.bc) = names(otu_split.N1.BC)
df.n.bc <- melt(dist.list.n.bc)
names(df.n.bc) <- c("Sample1", "Sample2", "BCdistance","Faecal_experiment")

df.n.bc$match = df.n.bc$Sample1 == df.n.bc$Sample2
df.n.bc.2 = df.n.bc[-which(df.n.bc$match == "TRUE"),]

litter.bc.boxplot <- ggplot(df.n.bc.2,aes(x = Faecal_experiment, y = BCdistance)) + 
  geom_jitter(position = position_jitter(0.3), aes(color = Faecal_experiment), alpha = 0.75) +
  geom_boxplot(size=1.0, fill='transparent') + 
  boxplot_theme +
  guides(colour = guide_legend(override.aes = list(size=6))) +
  labs(x = "Faecal experiment", y = "Bray-Curtis dissimilarity distances") +
  ggtitle("Litter samples", subtitle =  "PERMANOVA p = 1") +
  scale_color_manual(name = "Faecal removal",values= get_pal("Kakapo")) 
litter.bc.boxplot

litter.bc.boxplot.nojitter <- ggplot(df.n.bc.2,aes(x = Faecal_experiment, y = BCdistance)) + 
  geom_boxplot(size=1.0, aes(fill = Faecal_experiment)) + 
  boxplot_theme +
  labs(x = "Faecal experiment", y = "Bray-Curtis dissimilarity") +
  ggtitle("Litter samples", subtitle =  "PERMANOVA p = 1") +
  scale_fill_manual(name = "Bray-Curtis distances",values= get_pal("Kakapo")) 
litter.bc.boxplot.nojitter
#ggsave("FINAL/boxplots/fungi_bc_litter_pooR_nojitter.png", litter.bc.boxplot.nojitter, height = 10, width = 12, dpi = 400)
```

```{r fig.height= 9, fig.width=20}
library(ggpubr); packageVersion("ggpubr")
bc.boxplots.combined = ggarrange(faecal.bc.boxplot.nojitter, litter.bc.boxplot.nojitter, labels = c("A","B"), font.label = list(size = 30), 
          ncol=2, nrow=1, common.legend = T, legend = "bottom")
bc.boxplots.combined
ggsave("FINAL/boxplots/fungi_bc_boxplots_combined_nojitter_JUN2022.png", bc.boxplots.combined, width = 20, height = 9, dpi = 400)
```


##Taxa plots


```{r}
taxaplot_theme <-  theme_ipsum() + theme(plot.title = element_text(size = 35),
  
          axis.text.x = element_blank(),

          axis.ticks.x = element_blank(),

          axis.text.y=element_text(size=25),

          axis.title.y=element_text(size=35),
          
          axis.title.x = element_text(size=35),
          
          strip.text.x = element_text(size = 28),

          panel.grid.major = element_blank(),

          panel.grid.minor = element_blank(),

          panel.background = element_blank(),

          legend.box.background = element_rect(),

          legend.box.margin = margin(5, 5, 5, 5),

          legend.position="bottom",

          legend.title = element_text(face = "bold", size = 35),
          
          legend.text = element_text(size = 30))
```


```{r fig.cap = "K\u101k\u101p\u14d phylum others taxonomic plot", fig.height = 8, fig.width = 12, dpi=300}
library(plyr); packageVersion("plyr")
# get abundance in %
psF_RA <- transform_sample_counts(psF_SRS, function(x) x/sum(x))
psN_RA <- transform_sample_counts(psN_SRS, function(x) x/sum(x))
```
```{r}
glom_f <- tax_glom(psF_RA, taxrank = 'Taxonomy')

df_f <- psmelt(glom_f)
df_f$Taxonomy <- as.character(df_f$Taxonomy)
means_f <- ddply(df_f, ~Taxonomy, function(x) c(mean=mean(x$Abundance)))
remainder_f <- means_f[means_f$mean <= 0.003,]$Taxonomy 
df_f[df_f$Taxonomy %in% remainder_f,]$Taxonomy <- 'Other species <0.3%' 

print(levels(factor(df_f$Taxonomy)))
```


```{r fig.height = 20, fig.width = 40, dpi=300}
taxa.colours.f <- c("#882E72","#D6C1DE","#54809D","#4EB265","#CAE0AB","#77b6b1","#33605d","#F7EE55","#F9ECA0","#F6C141","#FF99AB","#FF0F39","#767676")

faecal_taxa <- ggplot(data=df_f, aes(x=Sample_Name, y=Abundance,  
                                         fill = factor(Taxonomy, 
                                                       c("Apiotrichum unclassified","Blastobotrys parvus",
                                                         "Blastobotrys unclassified","Candida albicans","Candida palmioleophila",
                                                         "Debaryomyces hansenii","Kazachstania telluris","Metschnikowia unclassified",
                                                         "Mycena flos-nivium","Spencermartinsiella unclassified","Thelebolus globosus",
                                                         "Vishniacozyma victoriae", "Other species <0.3%"))))


faecal_taxa_plotbar <- faecal_taxa + geom_bar(aes(), stat="identity", position="fill", width = 1)  + 
    guides(fill=guide_legend(title="Species", nrow = 4)) + taxaplot_theme + 
    theme(axis.title.y = element_blank(), axis.text.y = element_blank()) + 
    labs(x="K\u101k\u101p\u14d faecal samples") + 
    facet_grid(.~Age, scales = "free_x", space='free') +
    scale_fill_manual(values = taxa.colours.f)
faecal_taxa_plotbar

faecal_taxa_plotbar_age <- ggplot(data=df_f, 
                                  aes(x=Age, y=Abundance,  
                                      fill = factor(Taxonomy, 
                                                 c("Apiotrichum unclassified","Blastobotrys parvus",
                                                         "Blastobotrys unclassified","Candida albicans","Candida palmioleophila",
                                                         "Debaryomyces hansenii","Kazachstania telluris","Metschnikowia unclassified",
                                                         "Mycena flos-nivium","Spencermartinsiella unclassified","Thelebolus globosus",
                                                         "Vishniacozyma victoriae", "Other species <0.3%")))) + 
    geom_bar(aes(), stat="identity", position="fill", width = 1.5)  + 
    guides(fill=guide_legend(title="Species", nrow = 4)) + taxaplot_theme +
     theme(strip.text.x = element_blank()) +
    #theme(axis.text.x = element_text(size  = 18)) +
    ggtitle("Faecal samples by k\u101k\u101p\u14d chick age") +
    labs(y="Relative sequence abundance      ", x = "Age groups") +  
    facet_grid(.~Age, scales = "free_x", space='free') +
    scale_fill_manual(values = taxa.colours.f)
faecal_taxa_plotbar_age
```


```{r}
glom_nest.T <- tax_glom(psN_RA, taxrank = 'Taxonomy')

df_nest.T <- psmelt(glom_nest.T)
df_nest.T$Taxonomy <- as.character(df_nest.T$Taxonomy)
means_nest.T <- ddply(df_nest.T, ~Taxonomy, function(x) c(mean=mean(x$Abundance)))
remainder_nest.T <- means_nest.T[means_nest.T$mean <= 0.003,]$Taxonomy 
df_nest.T[df_nest.T$Taxonomy %in% remainder_nest.T,]$Taxonomy <- 'Other species <0.3%' 

print(levels(factor(df_nest.T$Taxonomy)))
```

```{r fig.cap = "K\u101k\u101p\u14d species others taxonomic plot", fig.height = 16, fig.width = 40, dpi=300}
nest.taxa.col <- c("#402060","#882E72","#D6C1DE","#54809D","#CAE0AB","#85CA95","#77b6b1","#008b8b","#33605d","#F9ECA0",
                   "#f3a833","#de5d3a","#9a4d76","#fa6e79","#ffa2ac","#ffd1d5","#6dead6","#36c5f4","#3388de","#e2dfdf","#767676")

taxa_plot_nest <- ggplot(data=df_nest.T, 
                         aes(x=Sample_Name, y=Abundance,  
                             fill = factor(Taxonomy, 
                                           c("Apiotrichum laibachii","Apiotrichum unclassified","Blastobotrys parvus",
                                             "Blastobotrys unclassified","Candida palmioleophila",
                                             "Cutaneotrichosporon dermatis","Debaryomyces hansenii","Geomyces auratus",
                                             "Kazachstania telluris","Leohumicola unclassified","Mortierella parvispora",
                                             "Mortierella unclassified","Oidiodendron unclassified","Penicillium spinulosum",
                                             "Priceomyces haplophilus","Pseudogymnoascus unclassified","Sistotrema coronilla",
                                             "Sugiyamaella unclassified","Trechispora unclassified","Umbelopsis isabellina",
                                             "Other species <0.3%")))) + 
    geom_bar(aes(), stat="identity", position="fill", width = 1)  +  
    guides(fill=guide_legend(title="Species", nrow = 7)) + taxaplot_theme + 
    theme(axis.title.y = element_blank(),axis.text.y = element_blank()) +
    labs(x = "Nest litter samples") +
    facet_grid(.~Age, scales = "free_x", space='free') +
    scale_fill_manual(values = nest.taxa.col)
taxa_plot_nest

taxa_plot_nest_age <- ggplot(data=df_nest.T, 
                         aes(x=Age, y=Abundance,  
                             fill = factor(Taxonomy, 
                                           c("Apiotrichum laibachii","Apiotrichum unclassified","Blastobotrys parvus",
                                             "Blastobotrys unclassified","Candida palmioleophila",
                                             "Cutaneotrichosporon dermatis","Debaryomyces hansenii","Geomyces auratus",
                                             "Kazachstania telluris","Leohumicola unclassified","Mortierella parvispora",
                                             "Mortierella unclassified","Oidiodendron unclassified","Penicillium spinulosum",
                                             "Priceomyces haplophilus","Pseudogymnoascus unclassified","Sistotrema coronilla",
                                             "Sugiyamaella unclassified","Trechispora unclassified","Umbelopsis isabellina",
                                             "Other species <0.3%")))) + 
    geom_bar(aes(), stat="identity", position="fill", width = 1.5)  + 
    guides(fill=guide_legend(title="Species", nrow = 5)) + taxaplot_theme + 
    ggtitle("Litter samples by days since first chick") +
    theme(axis.title.y=element_text(size=30), strip.text.x = element_blank()) +
    labs(y="Relative sequence abundance      ", x = "Temporal groups") +
    facet_wrap(~Age, scales = "free_x", nrow=1) +
    scale_fill_manual(values = nest.taxa.col)
taxa_plot_nest_age
```


```{r fig.height = 30, fig.width = 42, dpi=300}
taxa.f = ggarrange(faecal_taxa_plotbar_age, faecal_taxa_plotbar,  
          ncol=2, nrow=1, common.legend = T, legend = "bottom", widths = c(0.25,1))
taxa.f

taxa.n = ggarrange(taxa_plot_nest_age, taxa_plot_nest, 
          ncol=2, nrow=1, common.legend = T, legend = "bottom", widths = c(0.27,1))
taxa.n

taxa.combined = ggarrange(taxa.f, NULL, taxa.n, nrow = 3, labels = c("A","B"), font.label = list(size = 30), heights = c(1, 0.02, 1))
taxa.combined
ggsave("FINAL/taxa_plots/fungi_barplot_taxa_age_combined_JUN2022.png", taxa.combined, height = 30, width = 40, dpi=400)
```



##Alpha Diversity

####FAECAL
```{r}
rich_psF <- estimate_richness(psF_SRS, measures = c("Observed","InvSimpson"))
richF <- list(rich_psF, sample_data(psF_SRS)$NestFaeces, sample_data(psF_SRS)$Aspergillosis, sample_data(psF_SRS)$Movement, sample_data(psF_SRS)$Island, sample_data(psF_SRS)$Age, sample_data(psF_SRS)$Days, sample_data(psF_SRS)$Name, sample_data(psF_SRS)$Nest, sample_data(psF_SRS)$Nest_type, sample_data(psF_SRS)$Sample_Name)
names(richF) <- c("alpha_diversity", "NestFaeces", "Aspergillosis", "Movement", "Island", "Age", "Days", "Chick", "Nest", "Nest_type","Sample_Name")

shapiro.test(richF$alpha_diversity$Observed)
shapiro.test(richF$alpha_diversity$InvSimpson)

rich_dfF <- as.data.frame(richF)
names(rich_dfF)[names(rich_dfF) == "alpha_diversity.Observed"] <- "Observed"
names(rich_dfF)[names(rich_dfF) == "alpha_diversity.InvSimpson"] <- "InvSimpson"

# Faecal removal
kruskal.test(richF$alpha_diversity$Observed, richF$NestFaeces)
kruskal.test(richF$alpha_diversity$InvSimpson, richF$NestFaeces) 

# Aspergillosis
kruskal.test(richF$alpha_diversity$Observed, richF$Aspergillosis)
kruskal.test(richF$alpha_diversity$InvSimpson, richF$Aspergillosis) 

# Movement
kruskal.test(richF$alpha_diversity$Observed, richF$Movement)
kruskal.test(richF$alpha_diversity$InvSimpson, richF$Movement) 

# Island
richF.norear <- rich_dfF[-which(rich_dfF$Island == "Hand rearing"),]
kruskal.test(richF.norear$Observed, richF.norear$Island)
kruskal.test(richF.norear$InvSimpson, richF.norear$Island) 

# Age
kruskal.test(richF$alpha_diversity$Observed, richF$Age)
kruskal.test(richF$alpha_diversity$InvSimpson, richF$Age) 

#Nest type (without hand rearing samples)
richF.nt <- rich_dfF[-which(rich_dfF$Nest_type == "Hand rearing"| rich_dfF$Nest_type == "Sub-adult samples"),]

shapiro.test(richF.nt$Observed)
shapiro.test(richF.nt$InvSimpson)

kruskal.test(richF.nt$Observed, richF.nt$Nest_type)
kruskal.test(richF.nt$InvSimpson, richF.nt$Nest_type) 

#Nest
kruskal.test(richF.nt$Observed, richF.nt$Nest)
kruskal.test(richF.nt$InvSimpson, richF.nt$Nest)

# Chick
kruskal.test(richF$alpha_diversity$Observed, richF$Chick)
kruskal.test(richF$alpha_diversity$InvSimpson, richF$Chick) 
```

```{r}
library(dunn.test); packageVersion("dunn.test")

dunn.test(richF$alpha_diversity$Observed, richF$Aspergillosis, method = "bh") 

dunn.test(richF$alpha_diversity$Observed, richF$Island, method = "bh")
dunn.test(richF$alpha_diversity$InvSimpson, richF$Island, method = "bh")



dunn.test(richF$alpha_diversity$Observed, richF$Age, method = "bh")
dunn.test(richF$alpha_diversity$InvSimpson, richF$Age, method = "bh")

nest.Observed.pcs <- data.frame(dunn.test(richF.nt$Observed, richF.nt$Nest, method = "bh"))

dunn.test(richF_Nest_HR$alpha_diversity$InvSimpson, richF.nt$Nest_type, method = "bh")
```

####LITTER
```{r}
rich_psN_SRS <- estimate_richness(psN_SRS, measures = c("Observed","InvSimpson"))
richN <- list(rich_psN_SRS, sample_data(psN_SRS)$Name, sample_data(psN_SRS)$Aspergillosis, sample_data(psN_SRS)$Nest_type, sample_data(psN_SRS)$Age, sample_data(psN_SRS)$NestFaeces, sample_data(psN_SRS)$Movement, sample_data(psN_SRS)$Island,sample_data(psN_SRS)$Sample_Name)
names(richN) <- c("alpha_diversity", "Name", "Aspergillosis", "NestType", "Days","NestFaeces", "Movement", "Island","Sample_Name")

rich_dfN <- as.data.frame(richN)
names(rich_dfN)[names(rich_dfN) == "alpha_diversity.Observed"] <- "Observed"
names(rich_dfN)[names(rich_dfN) == "alpha_diversity.InvSimpson"] <- "InvSimpson"

shapiro.test(richN$alpha_diversity$Observed)
shapiro.test(richN$alpha_diversity$InvSimpson)

# NestFaeces 
kruskal.test(richN$alpha_diversity$Observed, richN$NestFaeces)
kruskal.test(richN$alpha_diversity$InvSimpson, richN$NestFaeces)

# Aspergillosis
kruskal.test(richN$alpha_diversity$Observed, richN$Aspergillosis)
kruskal.test(richN$alpha_diversity$InvSimpson, richN$Aspergillosis)

# Island
wilcox.test(richN$alpha_diversity$Observed ~ richN$Island) 
wilcox.test(richN$alpha_diversity$InvSimpson ~ richN$Island) 

# Movement
kruskal.test(richN$alpha_diversity$Observed, richN$Movement)
kruskal.test(richN$alpha_diversity$InvSimpson, richN$Movement)

# Days
kruskal.test(richN$alpha_diversity$Observed, richN$Days)
kruskal.test(richN$alpha_diversity$InvSimpson, richN$Days)

# NestType
kruskal.test(richN$alpha_diversity$Observed, richN$NestType)
kruskal.test(richN$alpha_diversity$InvSimpson, richN$NestType)

# Nest
kruskal.test(richN$alpha_diversity$Observed, richN$Name)
kruskal.test(richN$alpha_diversity$InvSimpson, richN$Name)
```

```{r}
dunn.test(richN$alpha_diversity$Observed, richN$Days, method = "bh")
dunn.test(richN$alpha_diversity$InvSimpson, richN$Days, method = "bh")
```

```{r}
faecal.obs.p.adj <- c("0.34","0.04","0.10","0.003","0.009","0.14","0.005","0.03")
faecal.invsimp..p.adj <- c("0.9","0.28","0.94","0.05","0.004","0.04","0.09","0.52")

p.adjust(faecal.obs.p.adj, method = "BH")
p.adjust(faecal.invsimp..p.adj, method="BH")

litter.obs.p.adj <- c("0.65","0.26","0.20","0.01","0.00001","0.31","0.27")
litter.invsimp..p.adj <- c("0.42","0.19","0.16","0.04","0.00001","0.39","0.44")

p.adjust(litter.obs.p.adj, method = "BH")
p.adjust(litter.invsimp..p.adj, method="BH")
```



###FAECAL PLOTS

```{r}
###FAECAL###
#nest.Observed.pcs[which(nest.Observed.pcs$P.adjusted < 0.05),]
Observed.F.nest <- data.frame(start=c("Atareta","Hoki"), 
                            end=c("Hoki","Marama"),
                            y=c(110,100),
                            label=c("0.02*","0.03*"))

Observed.F.asp <- data.frame(start=c("Unaffected","Unaffected"), 
                            end=c("Linked","Infected"),
                            y=c(130,150),
                            label=c("0.05","0.02*"))


Observed.F.Age <- data.frame(start=c("<20 days","<20 days"),
                              end=c("40 - 60 days","60 - 80 days"),
                              y=c(150,165),
                              label=c("**","*"))


invsimp.F.Age <- data.frame(start=c("<20 days","<20 days","20 - 40 days","40 - 60 days","60 - 80 days"),
                              end=c("40 - 60 days","60 - 80 days","200+ days","200+ days","200+ days"),
                              y=c(17.5,19.5,15.5,13.5,11.5),
                              label=c("*","*","**","**","**"))



myadptheme <- theme_ipsum() + theme(plot.title = element_text(size = 26),
  
          plot.subtitle = element_text(size = 24),
          
          axis.text.x = element_blank(),

          axis.title.x = element_text(size=35),

          axis.ticks.x = element_blank(),

          axis.text.y=element_text(size=25),

          axis.title.y=element_text(size=35),

          axis.line.x=element_line(color="black",size=1.0,linetype=1),

          axis.line.y=element_line(color="black",size=1.0,linetype=1),

          panel.grid.major = element_blank(),

          panel.grid.minor = element_blank(),

          panel.background = element_blank(),

          legend.box.background = element_rect(),

          legend.box.margin = margin(5, 5, 5, 5),

          legend.position="bottom",

          legend.title = element_text(face = "bold", size = 35),
          
          legend.text = element_text(size = 30))

```


```{r fig.height=10, fig.width=32}
kakapo_colours <- c("#4b5e1e", "#7D9D33", "#DCC949", "#BCA888", "#CD8862", "#775B24")

Observed_bar <- ggplot(data=rich_dfF, aes(x=Sample_Name,y=Observed, fill = Age)) + 
  
  geom_bar(aes(), stat="identity", position="stack", width = 1)  + 
  
  theme_ipsum() + theme(axis.text.x = element_blank(),

          axis.ticks.x = element_blank(),

          axis.text.y=element_blank(),

          axis.title.y=element_blank(),
          
          axis.title.x = element_text(size = 35),
          
          strip.text.x = element_blank(),
          
          panel.grid.major = element_blank(),

          panel.grid.minor = element_blank(),

          panel.background = element_blank(),
          
          axis.line.x=element_line(color="black",size=1.0,linetype=1),

          axis.line.y=element_blank(),
          
          legend.position = "none") +
  
  labs(x ="\nK\u101k\u101p\u14d faecal samples") + 
  
  scale_y_continuous(limits = c(0,200), expand = c(0, 0)) +
  
  facet_grid(~Age, scales = "free_x", space = "free")  + 
  
  scale_fill_manual(values = kakapo_colours)

Observed_bar
```

```{r fig.height=10, fig.width=10}
Observed.Age <- ggplot(rich_dfF, aes(x=Age, y=Observed))
Observed.Age.plot <- Observed.Age + geom_boxplot(size=1.0, aes(fill=Age)) + 
    myadptheme +
    theme(plot.title = element_text(size = 35)) +
    scale_fill_manual(values = kakapo_colours) + 
    labs(y = "Observed richness", x = "\nAge groups") +
    ggtitle("Kruskal-Wallis p = 0.02*") +
    geom_signif(data=Observed.F.Age,aes(xmin=start, xmax=end, annotations=label, y_position=y),
              manual=TRUE, tip_length = 0, textsize = 8, colour = "blue") 
Observed.Age.plot
```

```{r fig.height=10, fig.width=42}
Observed.faecal = ggarrange(Observed.Age.plot, Observed_bar, labels = c("B"), font.label = list(size = 30),
          ncol=2, nrow=1, legend = "none", widths = c(0.25,1))
Observed.faecal
```

```{r fig.height=10, fig.width=32}
invsimpson_bar <- ggplot(data=rich_dfF, aes(x=Sample_Name,y=InvSimpson, fill = Age)) + 
  
  geom_bar(aes(), stat="identity", position="stack", width = 1)  + 
  
  theme_ipsum() + theme(axis.text.x = element_blank(),

          axis.ticks.x = element_blank(),

          axis.text.y=element_blank(),

          axis.title.y=element_blank(),
          
          axis.title.x = element_text(size = 35),
          
          strip.text.x = element_blank(),
          
          panel.grid.major = element_blank(),

          panel.grid.minor = element_blank(),

          panel.background = element_blank(),
          
          axis.line.x=element_line(color="black",size=1.0,linetype=1),

          axis.line.y=element_blank(),
          
          legend.position = "bottom", 
          
          legend.title = element_text(face = "bold", size = 38),
          
          legend.text = element_text(size = 35),
          
          legend.box.background = element_rect(),

          legend.box.margin = margin(5, 5, 5, 5)) +
  
  labs(x = "\nK\u101k\u101p\u14d faecal samples") + 
  
  guides(fill = guide_legend(nrow = 1, override.aes=list(shape=15, size = 15))) +
  
  scale_y_continuous(limits = c(0,23), expand = c(0, 0)) +
  
  facet_grid(~Age, scales = "free_x", space = "free") + 
  
  scale_fill_manual(values = kakapo_colours)

invsimpson_bar

invsimpson_bar.NL <- invsimpson_bar + theme(legend.position = "none")

faecal.adp.legend <- get_legend(invsimpson_bar)
```

```{r fig.height=10, fig.width=10}
invsimp.Age <- ggplot(rich_dfF, aes(x=Age, y=InvSimpson))
invsimp.Age.plot <- invsimp.Age + geom_boxplot(size=1.0, aes(fill=Age)) + 
    myadptheme + 
    theme(plot.title = element_text(size = 35)) +
    scale_fill_manual(values = kakapo_colours) + 
    labs(y = "Inverse Simpson diversity", x = "\nAge groups") +
    ggtitle("Kruskal-Wallis p = 0.03*") +
    geom_signif(data=invsimp.F.Age,aes(xmin=start, xmax=end, annotations=label, y_position=y),
              manual=TRUE, tip_length = 0, textsize = 8, colour = "blue") 

invsimp.Age.plot
```

```{r fig.height=10, fig.width=42}
invsimp.faecal = ggarrange(invsimp.Age.plot, invsimpson_bar.NL, labels = c("C"), font.label = list(size = 30),
          ncol=2, nrow=1, legend = "none", widths = c(0.25,1))
invsimp.faecal
```

```{r fig.height = 40, fig.width = 42, dpi=300}
faecal.taxa.adp.combined = ggarrange(taxa.f, NULL, Observed.faecal,invsimp.faecal,faecal.adp.legend, nrow = 5, labels = c("A"), font.label = list(size = 30), heights = c(1, 0.02, 0.7, 0.7, 0.2))
faecal.taxa.adp.combined
ggsave("FINAL/taxa_plots/fungi_faecal_age_taxaplot_obs_JUN2022.png", faecal.taxa.adp.combined, height = 30, width = 42, dpi = 400, bg = "white")
```

```{r fig.cap = "Observed by nest", fig.height = 10, fig.width = 15, dpi=300}
nest.f.col <- c("#10121c","#2c1e31",'#6b2643',"#de5d3a","#e98537","#dab163","#e8d282","#f7f3b7","#26854c","#5ab552","#9de64e","#008b8b","#62a477","#a6cb96","#3e3b65","#3388de","#6dead6","#b0a7b8")

Observed.nest <- ggplot(richF.nt, aes(x=Nest, y=Observed))  
Observed.nest.plot <- Observed.nest + geom_boxplot(size=1.0, aes(fill=Nest)) + 
    myadptheme + theme(axis.title.x = element_text(size = 24), 
                                                 axis.title.y = element_text(size = 24), 
                                                 legend.text = element_text(size = 22), 
                                                 legend.title = element_text(size = 24)) +
    #scale_y_continuous(limits = c(1,330)) + 
    labs(y = "Observed richness", x = "Nest") +
    ggtitle("Observed", subtitle = "Kruskal-Wallis p = 0.02*") +
    scale_fill_manual(values = nest.f.col) +
    geom_signif(data=Observed.F.nest,aes(xmin=start, xmax=end, annotations=label, y_position=y),
              manual=TRUE, tip_length = 0, textsize = 5) 
Observed.nest.plot


invsimp.nest <- ggplot(richF.nt, aes(x=Nest, y=InvSimpson))  
invsimp.nest.plot <- invsimp.nest + geom_boxplot(size=1.0, aes(fill=Nest)) + 
    myadptheme + theme(axis.title.x = element_text(size = 24), 
                                                 axis.title.y = element_text(size = 24), 
                                                 legend.text = element_text(size = 22), 
                                                 legend.title = element_text(size = 24)) +
    labs(y = "Inverse Simpson diversity", x = "Nest") + 
    ggtitle("Inverse Simpson",subtitle = "Kruskal-Wallis p = 0.14") +
    scale_fill_manual(values = nest.f.col)
invsimp.nest.plot
```



```{r fig.height = 21, fig.width = 15, dpi=300}
library(grid)
nest.f = ggarrange(Observed.nest.plot, invsimp.nest.plot, labels = c("A","B"), font.label = list(size = 30),  
          ncol=1, nrow=2, common.legend = TRUE, legend="bottom")
nest.f.title = annotate_figure(nest.f, top = text_grob("Faecal by nest of residence", face = "bold", family = "sans", size = 30))
nest.f.title

ggsave("FINAL/alpha_div/faecal_nest_adp_JUN2022.png",nest.f.title, height = 21, width = 15, dpi = 400)
```


```{r}
myadptheme.edit <- theme_ipsum() + theme(plot.title = element_text(size = 28),
                                         
          plot.subtitle = element_text(size = 25),
  
          axis.text.x = element_blank(),

          axis.title.x = element_text(size=24),

          axis.ticks.x = element_blank(),

          axis.text.y=element_text(size=20),

          axis.title.y=element_text(size=24),

          axis.line.x=element_line(color="black",size=1.0,linetype=1),

          axis.line.y=element_line(color="black",size=1.0,linetype=1),

          panel.grid.major = element_blank(),

          panel.grid.minor = element_blank(),

          panel.background = element_blank(),

          legend.box.background = element_rect(),

          legend.box.margin = margin(5,5,5,5),

          legend.position="bottom",

          legend.title = element_text(face = "bold", size = 26),
          
          legend.text = element_text(size = 24))
```


```{r fig.cap = "combined faecal with pooled samples", fig.height = 10, fig.width = 8, dpi=300}
##Aspergillosis
Observed.asp <- ggplot(rich_dfF, aes(x=Aspergillosis, y=Observed))
Observed.asp.plot <- Observed.asp + geom_boxplot(size=1.0, aes(fill=Aspergillosis)) + myadptheme.edit + 
    theme(plot.margin = unit(c(2,0.5,0.5,0.5), "cm")) + 
    labs(y="Observed richness", x = "Aspergillosis") +
    scale_fill_manual(values= c("#7D9D33", "#CED38C", "#CD8862")) + 
    ggtitle("Observed", subtitle = "Kruskal-Wallis p = 0.06") 
Observed.asp.plot

invsimp.asp <- ggplot(rich_dfF, aes(x=Aspergillosis, y=InvSimpson))
invsimp.asp.plot <- invsimp.asp + geom_boxplot(size=1.0, aes(fill=Aspergillosis)) + myadptheme.edit + 
    theme(plot.margin = unit(c(2,0.5,0.5,0.5), "cm")) +
    labs(y = "Inverse Simpson diversity", x = "Aspergillosis") + 
    ggtitle("Inverse Simpson", subtitle = "Kruskal-Wallis p = 0.45") + 
    scale_fill_manual(values= c("#7D9D33", "#CED38C", "#CD8862")) 
invsimp.asp.plot

##Location
Observed.location <- ggplot(richF.norear, aes(x=Island, y=Observed))
Observed.location.plot <- Observed.location + geom_boxplot(size=1.0, aes(fill=Island)) + myadptheme.edit + 
    theme(plot.margin = unit(c(2,0.5,0.5,0.5), "cm")) + 
    labs(y="Observed richness", x = "Location") +
    scale_fill_manual(values= c("#4B5F6C", "#A8B9CB"), name = "Location") +
    ggtitle("Observed", subtitle = "Wilcoxon p = 0.02*") 
Observed.location.plot

invsimp.location <- ggplot(richF.norear, aes(x=Island, y=InvSimpson))
invsimp.location.plot <- invsimp.location + geom_boxplot(size=1.0, aes(fill=Island)) + myadptheme.edit +
    theme(plot.margin = unit(c(2,0.5,0.5,0.5), "cm")) +
    scale_y_continuous(limits = c(0,22)) +
    labs(y = "Inverse Simpson diversity",  x = "Location") +
    scale_fill_manual(values= c("#4B5F6C", "#A8B9CB"), name = "Location") + 
    ggtitle("Inverse Simpson", subtitle = "Wilcoxon p = 0.13")
invsimp.location.plot
```


###LITTER PLOTS

```{r}
Observed.N.days <- data.frame(start=c("<20 days","<20 days"),
                              end=c("40 - 60 days","60 - 90 days"),
                              y=c(175,195),
                              label=c("**","*"))

invsimp.N.days <- data.frame(start=c("<20 days","<20 days","<20 days"),
                              end=c("20 - 40 days","40 - 60 days","60 - 90 days"),
                              y=c(1.5,1.65,1.8),
                              label=c("**","**","**"))


nest.col <- c("#882E72","#ffd1d5","#D6C1DE","#54809D","#4EB265","#CAE0AB","#77b6b1","#33605d","#F7EE55","#F6C141","#e98537","#FF99AB","#FF0F39","#ac2847","#767676")
```

```{r fig.height=10, fig.width=32}
kakapo_colours <- c("#4b5e1e", "#7D9D33", "#DCC949", "#BCA888", "#CD8862", "#775B24")

Observed_bar.litter <- ggplot(data=rich_dfN, aes(x=Sample_Name,y=Observed, fill = Days)) + 
  
  geom_bar(aes(), stat="identity", position="stack", width = 1)  + #scale_y_log10() +
  
  theme_ipsum() + theme(axis.text.x = element_blank(),

          axis.ticks.x = element_blank(),

          axis.text.y=element_blank(),

          axis.title.y=element_blank(),
          
          axis.title.x = element_text(size = 35),
          
          strip.text.x = element_blank(),
          
          panel.grid.major = element_blank(),

          panel.grid.minor = element_blank(),

          panel.background = element_blank(),
          
          axis.line.x=element_line(color="black",size=1.0,linetype=1),

          axis.line.y=element_blank(),
          
          legend.position = "none") +
  
  labs(x="\nNest litter samples") + 
  
  scale_y_continuous(limits = c(0,225), expand = c(0, 0)) +
  
  facet_grid(~Days, scales = "free_x", space = "free")  + 
  
  #scale_x_discrete(labels = as.character(rich_dfF$annotate_2)) +
  
  scale_fill_manual(values = kakapo_colours, name = "Days since first chick")

Observed_bar.litter
```

```{r fig.height=10, fig.width=10}
Observed.days.litter <- ggplot(rich_dfN, aes(x=Days, y=Observed))
Observed.days.litter.plot <- Observed.days.litter + geom_boxplot(size=1.0, aes(fill=Days)) + 
    myadptheme + theme(plot.title = element_text(size = 35)) +
    scale_fill_manual(values = kakapo_colours, name = "Days since first chick") + 
    labs(y = "Observed richness", x = "\nTemporal groups") +
    ggtitle("Kruskal-Wallis p < 0.001***") +
    geom_signif(data=Observed.N.days,aes(xmin=start, xmax=end, annotations=label, y_position=y),
              manual=TRUE, tip_length = 0, textsize = 8, color = "blue")
Observed.days.litter.plot
```

```{r fig.height=10, fig.width=42}
Observed.litter = ggarrange(Observed.days.litter.plot, Observed_bar.litter, labels = c("B"), font.label = list(size = 30),
          ncol=2, nrow=1, legend = "none", widths = c(0.27,1))
Observed.litter
```

```{r fig.height=10, fig.width=32}
rich_dfN$InvSimpsonlog = log10(rich_dfN$InvSimpson)

invsimpson_bar.litter <- ggplot(data=rich_dfN, aes(x=Sample_Name,y=InvSimpsonlog, fill = Days)) + 
  
  geom_bar(aes(), stat="identity", position="stack", width = 1)  + 
  
  theme_ipsum() + theme(axis.text.x = element_blank(),

          axis.ticks.x = element_blank(),

          axis.text.y=element_blank(),

          axis.title.y=element_blank(),
          
          axis.title.x = element_text(size = 35),
          
          strip.text.x = element_blank(),
          
          panel.grid.major = element_blank(),

          panel.grid.minor = element_blank(),

          panel.background = element_blank(),
          
          axis.line.x=element_line(color="black",size=1.0,linetype=1),

          axis.line.y=element_blank(),
          
          legend.position = "bottom", 
          
          legend.title = element_text(face = "bold", size = 38),
          
          legend.text = element_text(size = 35),
          
          legend.box.background = element_rect(),

          legend.box.margin = margin(5, 5, 5, 5)) +
  
  labs(x = "\nNest litter samples") +
  
   guides(fill = guide_legend(nrow = 1, override.aes=list(shape=15, size = 15))) +
  
  scale_y_continuous(expand = c(0, 0), limits = c(0, 2)) +
  
  facet_grid(~Days, scales = "free_x", space = "free") + 
  
  scale_fill_manual(values = kakapo_colours, name = "Days")

invsimpson_bar.litter

invsimpson_bar.NL.litter <- invsimpson_bar.litter + theme(legend.position = "none")

litter.adp.legend <- get_legend(invsimpson_bar.litter)
```

```{r fig.height=10, fig.width=10}
invsimp.days.litter <- ggplot(rich_dfN, aes(x=Days, y=InvSimpsonlog))
invsimp.days.litter.plot <- invsimp.days.litter + geom_boxplot(size=1.0, aes(fill=Days)) + 
    myadptheme + theme(plot.title = element_text(size = 35)) +
    scale_fill_manual(values = kakapo_colours, name = "Days since first chick") + 
    labs(y = "Inverse Simpson diversity [log10]", x = "\nTemporal groups") +
    ggtitle("Kruskal-Wallis p < 0.001***") +
    geom_signif(data=invsimp.N.days,aes(xmin=start, xmax=end, annotations=label, y_position=y),
              manual=TRUE, tip_length = 0, textsize = 8, colour = "blue") 

invsimp.days.litter.plot
```

```{r fig.height=10, fig.width=42}
invsimp.litter = ggarrange(invsimp.days.litter.plot, invsimpson_bar.NL.litter, labels = c("C"), font.label = list(size = 30),
          ncol=2, nrow=1, legend = "none", widths = c(0.27,1))
invsimp.litter
```

```{r fig.height = 40, fig.width = 42, dpi=300}
litter.taxa.adp.combined = ggarrange(taxa.n, NULL, Observed.litter,invsimp.litter,litter.adp.legend, nrow = 5, labels = c("A"), font.label = list(size = 30), heights = c(1, 0.02, 0.7, 0.7, 0.2))
litter.taxa.adp.combined
ggsave("FINAL/taxa_plots/fungi_litter_age_taxaplot_obs_JUN2022.png", litter.taxa.adp.combined, height = 30, width = 42, dpi = 400, bg = "white")
```


```{r fig.cap = "nest alpha diversity", fig.height = 21, fig.width = 15, dpi=300}
nest.f.col.litter <- c("#10121c","#2c1e31","#de5d3a","#e98537","#dab163","#e8d282","#f7f3b7","#26854c","#5ab552","#9de64e","#008b8b","#62a477","#3e3b65","#3388de","#b0a7b8")


Observed.nest.name <- ggplot(rich_dfN, aes(x=Name, y=Observed))  
Observed.nest.name.plot <- Observed.nest.name + geom_boxplot(size=1.0, aes(fill=Name)) + 
    myadptheme + theme(axis.title.x = element_text(size = 24), 
                                                 axis.title.y = element_text(size = 24), 
                                                 legend.text = element_text(size = 22), 
                                                 legend.title = element_text(size = 24)) +
    labs(y="Observed richness", x = "Nest") +
    ggtitle("Observed", subtitle = "Kruskal-Wallis p = 0.36") +
    scale_fill_manual(values = nest.f.col.litter, name = "Nest") 
Observed.nest.name.plot

invsimp.nest.name <- ggplot(rich_dfN, aes(x=Name, y=InvSimpson))  
invsimp.nest.name.plot <- invsimp.nest.name + geom_boxplot(size=1.0, aes(fill=Name)) + 
     myadptheme + theme(axis.title.x = element_text(size = 24), 
                                                 axis.title.y = element_text(size = 24), 
                                                 legend.text = element_text(size = 22), 
                                                 legend.title = element_text(size = 24)) +
     ggtitle("Inverse Simpson", subtitle = "Kruskal-Wallis p = 0.44") + 
     labs(y = "Inverse Simpson diversity", x = "Nest") +
     scale_fill_manual(values = nest.f.col.litter,name = "Nest") 

nest.name <- ggarrange(Observed.nest.name.plot, invsimp.nest.name.plot, labels = c("A","B"), font.label = list(size = 30), 
          ncol=1, nrow=2, common.legend = TRUE, legend="bottom")
nest.name.title = annotate_figure(nest.name, top = text_grob("Litter samples by nest", face = "bold", family = "sans", size = 30))
nest.name.title

ggsave("FINAL/alpha_div/litter_nest_adp_JUN2022.png",nest.name.title, height = 21, width = 15, dpi = 400)
```
``

```{r fig.cap = "Alpha Diversity combined nest", fig.height = 10, fig.width = 8, dpi=300}
##Aspergillosis
Observed.asp.nest <- ggplot(rich_dfN, aes(x=Aspergillosis, y=Observed))
Observed.asp.nest.plot <- Observed.asp.nest + geom_boxplot(size=1.0, aes(fill=Aspergillosis)) + myadptheme.edit + 
  theme(plot.margin = unit(c(2,0.5,0.5,0.5), "cm")) + labs(y="Observed richness", x = "Aspergillosis") +
  scale_fill_manual(values= c("#7D9D33", "#CED38C", "#CD8862")) + 
  ggtitle("Observed", subtitle = "Kruskal-Wallis p = 0.36") 
Observed.asp.nest.plot

invsimp.asp.nest <- ggplot(rich_dfN, aes(x=Aspergillosis, y=InvSimpson))
invsimp.asp.nest.plot <- invsimp.asp.nest + geom_boxplot(size=1.0, aes(fill=Aspergillosis), outlier.shape = NA) + 
  myadptheme.edit + 
  scale_y_continuous(limits = c(1,5)) +
  theme(plot.margin = unit(c(2,0.5,0.5,0.5), "cm")) +
  labs(y = "Inverse Simpson diversity", x = "Aspergillosis") + 
  ggtitle("Inverse Simpson", subtitle = "Kruskal-Wallis p = 0.33") + 
  scale_fill_manual(values= c("#7D9D33", "#CED38C", "#CD8862")) 
invsimp.asp.nest.plot

##Location
Observed.location.nest <- ggplot(rich_dfN, aes(x=Island, y=Observed))
Observed.location.nest.plot <- Observed.location.nest + geom_boxplot(size=1.0, aes(fill=Island)) + myadptheme.edit + 
    theme(plot.margin = unit(c(2,0.5,0.5,0.5), "cm")) + labs(y="Observed richness", x = "Location") +
    scale_fill_manual(values= c("#4B5F6C", "#A8B9CB"),name = "Location") +
    ggtitle("Observed", subtitle = "Wilcoxon p = 0.04*") 
Observed.location.nest.plot

invsimp.location.nest <- ggplot(rich_dfN, aes(x=Island, y=InvSimpson))
invsimp.location.nest.plot <- invsimp.location.nest + geom_boxplot(size=1.0, aes(fill=Island), outlier.shape = NA) + 
    scale_y_continuous(limits = c(1,5)) +
    myadptheme.edit +
    theme(plot.margin = unit(c(2,0.5,0.5,0.5), "cm")) +
    labs(y = "Inverse Simpson diversity", x = "Location") +
    scale_fill_manual(values= c("#4B5F6C", "#A8B9CB"), name = "Location") + 
    ggtitle("Inverse Simpson", subtitle = "Wilcoxon p = 0.14")
invsimp.location.nest.plot
```


```{r fig.height = 35, fig.width = 17, dpi=300}
asp.f = ggarrange(Observed.asp.plot, invsimp.asp.plot, labels = c("A"), font.label = list(size = 30),  
          ncol=2, nrow=1, common.legend = TRUE, legend="bottom")

location.f = ggarrange(Observed.location.plot, invsimp.location.plot, labels = c("B"),  font.label = list(size = 30), 
          ncol=2, nrow=1, common.legend = TRUE, legend="bottom")

asp.nest = ggarrange(Observed.asp.nest.plot, invsimp.asp.nest.plot, labels = c("C"),  font.label = list(size = 30), 
          ncol=2, nrow=1, common.legend = TRUE, legend="bottom")

location.nest = ggarrange(Observed.location.nest.plot, invsimp.location.nest.plot, labels = c("D"),  font.label = list(size = 30), 
          ncol=2, nrow=1, common.legend = TRUE, legend="bottom")

library(gridExtra)
faecal.together <- grid.arrange(asp.f,location.f,
                              nrow = 2, top=textGrob("Faecal samples",
                                                     gp=gpar(fontsize=30,fontfamily="sans",fontface="bold")))
nest.together <- grid.arrange(asp.nest, location.nest,
                              nrow = 2, top=textGrob("Litter samples",
                                                     gp=gpar(fontsize=30,fontfamily="sans",fontface="bold")))

library(cowplot); packageVersion("cowplot")
combined.adp <- plot_grid(faecal.together, NULL, nest.together, nrow = 3, rel_heights = c(1,0.05,1))
combined.adp

ggsave("FINAL/alpha_div/combined_asp_loc_adp_JUN2022.png",combined.adp, height = 30, width = 20, dpi = 400, bg = "white")
```


#Heat maps

```{r}
heatmap.theme <- theme_ipsum() + theme(plot.title = element_text(size = 24),
  
          axis.ticks.x = element_blank(),

          axis.text.y=element_text(size=14),
          
          axis.text.x=element_text(size=17),

          axis.title.y=element_text(size=20),
          
          axis.title.x = element_text(size=20),
          
          panel.grid.major = element_blank(),

          panel.grid.minor = element_blank(),

          panel.background = element_blank(),
          
          legend.position = "right",
          
          legend.title = element_text(size = 17),
          
          legend.text = element_text(size = 12))
```

```{r fig.height = 20, fig.width = 16, dpi=300}
psF_SRS_norear <- subset_samples(psF_SRS, Island != "Hand rearing")
merged.ps.F.island <- merge_samples(psF_SRS_norear, "Island")
top20.F.island <- prune_taxa(names(sort(taxa_sums(merged.ps.F.island),TRUE)[1:20]), merged.ps.F.island)

hm.f.is = plot_heatmap(top20.F.island, "PCoA","bray", low="#ffd1d5", high="#6b2643", na.value="#f6e8e0",
                        taxa.order="Family", sample.order = c("Pukenui","Whenua Hou")) + 
      theme_ipsum() + 
      labs(x = "Location", y = "ASV") + 
      heatmap.theme + 
      ggtitle("Faecal samples")
hm.f.is

merged.ps.N.island <- merge_samples(psN_SRS, "Island")
top20.N.island <- prune_taxa(names(sort(taxa_sums(merged.ps.N.island),TRUE)[1:20]), merged.ps.N.island)

hm.n.is = plot_heatmap(top20.N.island, "PCoA","bray", low="#CAE0AB", high="#33605d", na.value="#f4f8ee", taxa.order="Family") + 
      theme_ipsum() + 
      labs(x = "Location", y = "ASV") + 
      heatmap.theme + 
      ggtitle("Litter samples")
hm.n.is

heatmap.combined.is <- ggarrange(hm.f.is, hm.n.is, nrow = 2, labels = c("A","B"), font.label = list(size = 30)) + theme(plot.margin = margin(3,0.5,0.5,0.5, "cm"))
heatmap.combined.is
ggsave("FINAL/heatmap_location_combined_JUN2022.png", heatmap.combined.is, width = 16, height = 20, dpi = 400)
```

```{r fig.height = 10, fig.width = 16}
merged.ps.F.age <- merge_samples(psF_SRS, "Age")
top20.F.age <- prune_taxa(names(sort(taxa_sums(merged.ps.F.age),TRUE)[1:20]), merged.ps.F.age)

hm.f.age = plot_heatmap(top20.F.age, "PCoA","bray", low="#ffd1d5", high="#6b2643", na.value="#f6e8e0",
                        taxa.order="Family", sample.order = c("<20 days","20 - 40 days","40 - 60 days", "60 - 80 days", "200+ days")) + 
      theme_ipsum() + 
      labs(x = "K\u101k\u101p\u14d chick age", y = "ASV") + 
      heatmap.theme + 
      ggtitle("Faecal samples")
hm.f.age

merged.ps.N.days <- merge_samples(psN_SRS, "Age")
top20.N.days <- prune_taxa(names(sort(taxa_sums(merged.ps.N.days),TRUE)[1:20]), merged.ps.N.days)

hm.n.days = plot_heatmap(top20.N.days, "PCoA","bray", low="#CAE0AB", high="#33605d", na.value="#f4f8ee", taxa.order="Family",
                         sample.order = c("<20 days","20 - 40 days","40 - 60 days", "60 - 90 days")) + 
      theme_ipsum() + 
      labs(x = "Days since first chick", y = "ASV") + 
      heatmap.theme + 
      ggtitle("Litter samples")
hm.n.days


library(ggpubr)
heatmap.combined.age <- ggarrange(hm.f.age, hm.n.days, nrow = 2, labels = c("A","B"), font.label = list(size = 30)) + theme(plot.margin = margin(3,0.5,0.5,0.5, "cm"))
ggsave("FINAL/heatmap_age_combined_JUN2022.png", heatmap.combined.age, width = 16, height = 20, dpi = 400)
```


#Beta Diversity

```{r}
library(ggtext)
ordplot_theme = theme_ipsum() + 
  theme(plot.title = element_markdown(size = 32, margin=margin(0,0,30,0)),
    
    axis.title.x = element_text(size=25),
    
    axis.title.y =element_text(size=25),
    
    axis.text.x = element_text(size = 17),
    
    axis.text.y = element_text(size = 17),

    axis.line.x=element_line(color="black",size=0.5,linetype=1),

    axis.line.y=element_line(color="black",size=0.5,linetype=1),

    panel.grid.major = element_blank(),

    panel.grid.minor = element_blank(),

    panel.background = element_blank(),

    legend.text = element_markdown(size=25),
    
    legend.title = element_markdown(face="bold", size = 28),
    
    legend.position = "top") 
```

###PCOA with Vectors

```{r}
map.f.2 <- sample_data(psF_SRS)
identical(rownames(map.f.2), rownames(SRS_outputF.df.sort))
map.f.2$K_abundance = SRS_outputF.df.sort$`ASV_1_Kazachstania telluris`
psF_SRS_beta <- phyloseq(otu_table(SRS_outputF.df.sort, taxa_are_rows = F), 
                sample_data(map.f.2),
                tax_table(NtaxaF.df))

psF_RA <- transform_sample_counts(psF_SRS_beta, function(x) {x/sum(x)})

map.n.2 <- sample_data(psN_SRS)
identical(rownames(map.n.2), rownames(SRS_outputN.df.sort))
map.n.2$D_abundance = SRS_outputN.df.sort$`ASV_1_Debaryomyces hansenii`
map.n.2$A_abundance = SRS_outputN.df.sort$`ASV_2_Apiotrichum unclassified`
psN_SRS_beta <- phyloseq(otu_table(SRS_outputN.df.sort, taxa_are_rows = F), 
                sample_data(map.n.2),
                tax_table(NtaxaN.df))

psN_RA <- transform_sample_counts(psN_SRS_beta, function(x) {x/sum(x)})
```


####Faecal
```{r results='hide'}
library(vegan)
F_otu_RA <- data.frame(otu_table(psF_RA))
F.dist <- vegdist(F_otu_RA, method="bray",
                    binary=FALSE, diag=FALSE, upper=FALSE,
                    na.rm=FALSE)

pcoa_bactF<-cmdscale(F.dist, k=2, eig=T)
pcoa.var.perF<-round(pcoa_bactF$eig/sum(pcoa_bactF$eig)*100, 1)

pcoa.valuesF <- pcoa_bactF$points

pcoa.dataF <- data.frame(Sample=rownames(pcoa.valuesF),
                        X=pcoa.valuesF[,1],
                        Y=pcoa.valuesF[,2])

pcoa.mapF <- data.frame(sample_data(psF_RA))

pcoa.dataF$Name <- pcoa.mapF$Name
pcoa.dataF$Nest <- pcoa.mapF$Nest
pcoa.dataF$Age <- pcoa.mapF$Age
pcoa.dataF$Aspergillosis <- pcoa.mapF$Aspergillosis
pcoa.dataF$NestFaeces <- pcoa.mapF$NestFaeces
pcoa.dataF$Nest_type <- pcoa.mapF$Nest_type
pcoa.dataF$Movement <- pcoa.mapF$Movement
pcoa.dataF$K_abundance <- pcoa.mapF$K_abundance
pcoa.dataF$Island <- pcoa.mapF$Island


vec.spF<-envfit(pcoa_bactF$points , F_otu_RA, perm=1000)

vec.sp.df_F<-
  as.data.frame(scores(vec.spF, "vectors"))

vec.sp.df_F$species<-rownames(vec.sp.df_F)


vec.sp.df_F.sig <- vec.sp.df_F[c(1:5,21,33,319), ]
```

```{r fig.height = 10, fig.width = 18, dpi=300}
taxa.f.loc <- ggplot(data=pcoa.dataF, aes(x = X, y = Y, colour = Island)) +
  geom_point(size=7, aes(shape=Aspergillosis)) +
  xlab(paste("PCoA 1","[" ,pcoa.var.perF[1], "%","]" ,sep=" ")) +
  ylab(paste("PCoA 2","[" ,pcoa.var.perF[2], "%","]" ,sep=" ")) + 
  geom_vline(xintercept = 0, linetype = "dashed") + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_manual(values = c("#61818e","#8e6181","#818e61"), name="Location") + 
  scale_shape_manual(values=c(15:17)) +
  ordplot_theme + theme(legend.box = "vertical") + 
  guides(shape = guide_legend(order = 1)) +
  ggtitle("Faecal samples by location")

taxa.f.loc
```

```{r fig.height = 10, fig.width = 18, dpi=300}
taxa.f.kaz <- ggplot(data=pcoa.dataF, aes(x = X, y = Y, colour = K_abundance)) +
  geom_point(size=7, aes(shape=Aspergillosis)) +
  xlab(paste("PCoA 1","[" ,pcoa.var.perF[1], "%","]" ,sep=" ")) +
  ylab(paste("PCoA 2","[" ,pcoa.var.perF[2], "%","]" ,sep=" ")) + 
  geom_vline(xintercept = 0, linetype = "dashed") + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_shape_manual(values=c(15:17)) +
  ordplot_theme + theme(legend.box = "vertical") + 
  guides(shape = guide_legend(order = 1)) +
  scale_color_gradient(low = "blue", high = "red", name="*K. telluris* abundance",
                       labels=c("Low","High"),breaks=c(75,420), guide = "colourbar") +
  ggtitle("Faecal samples by ASV1 *K. telluris* abundance")

taxa.f.kaz
```

```{r fig.height = 10, fig.width = 18, dpi=300}
taxa.f.age <- ggplot(data=pcoa.dataF, aes(x = X, y = Y, colour = Age)) +
  geom_point(size=7, aes(shape=Aspergillosis)) +
  xlab(paste("PCoA 1","[" ,pcoa.var.perF[1], "%","]" ,sep=" ")) +
  ylab(paste("PCoA 2","[" ,pcoa.var.perF[2], "%","]" ,sep=" ")) + 
  geom_vline(xintercept = 0, linetype = "dashed") + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_manual(values = c("#788374","#ebd27d","#aa644d","#372a39","#597692","#5a5145")) + 
  scale_shape_manual(values=c(15:17)) +
  ordplot_theme + theme(legend.box = "vertical") + 
  guides(color = guide_legend(nrow = 2), shape = guide_legend(order = 1)) +
  ggtitle("Faecal samples by k\u101k\u101p\u14d chick age")

taxa.f.age
```

```{r fig.height = 10, fig.width = 18, dpi=300}
taxa.f.vec <- ggplot(data=pcoa.dataF, aes(x = X, y = Y)) +
  xlab(paste("PCoA 1","[" ,pcoa.var.perF[1], "%","]" ,sep=" ")) +
  ylab(paste("PCoA 2","[" ,pcoa.var.perF[2], "%","]" ,sep=" ")) + 
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_segment(data=vec.sp.df_F.sig,
               aes(x=0,xend=Dim1,y=0,yend=Dim2),
               arrow = arrow(length = unit(0.3, "cm")),
               colour="red", size = 1,
               inherit.aes=FALSE) +
  geom_text_repel(data=vec.sp.df_F.sig,
            aes(x=Dim1,y=Dim2,label=species),size=7.5,
            inherit.aes=FALSE) +
  ordplot_theme +
       ylim(-0.72, 0.7) +
       xlim(-0.77, 1.1) +
  ggtitle("Influential ASV vectors for ordinated faecal samples")

taxa.f.vec
```

```{r fig.height = 24, fig.width = 36, dpi=300}
pcoa_faecal_ords <-  ggarrange(taxa.f.loc, taxa.f.kaz, taxa.f.age, taxa.f.vec, labels = c("A","B","C","D"), ncol = 2, nrow=2, font.label = list(size = 30))
pcoa_faecal_ords
ggsave("FINAL/ordinations/taxa_vectors_faecal_edit_SEPT.png", pcoa_faecal_ords, width = 36, height = 20, dpi = 400, bg = "white")
```


####Nest
```{r results='hide'}
N_otu_RA <- data.frame(otu_table(psN_RA))
N.dist <- vegdist(N_otu_RA, method="bray",
                    binary=FALSE, diag=FALSE, upper=FALSE,
                    na.rm=FALSE)

pcoa_bactN<-cmdscale(N.dist, k=2, eig=T)
pcoa.var.perN<-round(pcoa_bactN$eig/sum(pcoa_bactN$eig)*100, 1)

pcoa.valuesN <- pcoa_bactN$points

pcoa.dataN <- data.frame(Sample=rownames(pcoa.valuesN),
                        X=pcoa.valuesN[,1],
                        Y=pcoa.valuesN[,2])

pcoa.mapN <- data.frame(sample_data(psN_RA))

pcoa.dataN$Name <- pcoa.mapN$Name
pcoa.dataN$Nest <- pcoa.mapN$Nest
pcoa.dataN$Aspergillosis <- pcoa.mapN$Aspergillosis
pcoa.dataN$Nest_type <- pcoa.mapN$Nest_type
pcoa.dataN$Age <- pcoa.mapN$Age
pcoa.dataN$D_abundance <- pcoa.mapN$D_abundance
pcoa.dataN$A_abundance <- pcoa.mapN$A_abundance
pcoa.dataN$Island <- pcoa.mapN$Island

vec.spN<-envfit(pcoa_bactN$points , N_otu_RA, perm=1000)

vec.sp.df_N<-
  as.data.frame(scores(vec.spN, "vectors"))

vec.sp.df_N$species<-rownames(vec.sp.df_N)


vec.sp.df_N.sig <- vec.sp.df_N[c(1:5,86,89,354,365), ]
```

```{r fig.height = 10, fig.width = 18, dpi=300}
taxa.n.loc <- ggplot(data=pcoa.dataN, aes(x = X, y = Y, colour = Island)) +
  geom_point(size=7, aes(shape=Aspergillosis)) +
  xlab(paste("PCoA 1","[" ,pcoa.var.perN[1], "%","]" ,sep=" ")) +
  ylab(paste("PCoA 2","[" ,pcoa.var.perN[2], "%","]" ,sep=" ")) + 
   geom_vline(xintercept = 0, linetype = "dashed") + 
   geom_hline(yintercept = 0, linetype = "dashed") +
  # geom_segment(data=vec.sp.df_F.sig, 
  #              aes(x=0,xend=Dim1,y=0,yend=Dim2),
  #              arrow = arrow(length = unit(0.3, "cm")),
  #              colour="red", size = 1,
  #              inherit.aes=FALSE) + 
  # geom_text(data=vec.sp.df_F.sig,
  #           aes(x=Dim1,y=Dim2,label=species),size=4,
  #           inherit.aes=FALSE) + 
  scale_color_manual(values = c("#8e6181","#818e61"), name="Location") + 
  scale_shape_manual(values=c(15:17)) +
  ordplot_theme + theme(legend.box = "vertical") + 
  guides(shape = guide_legend(order = 1)) +
  #   ylim(-0.5, 0.75) +
  # xlim(-0.58, 0.96) +
  ggtitle("Litter samples by island")

taxa.n.loc
```

```{r fig.height = 10, fig.width = 18, dpi=300}
taxa.n.deb <- ggplot(data=pcoa.dataN, aes(x = X, y = Y, colour = D_abundance)) +
  geom_point(size=7, aes(shape=Aspergillosis)) +
  xlab(paste("PCoA 1","[" ,pcoa.var.perN[1], "%","]" ,sep=" ")) +
  ylab(paste("PCoA 2","[" ,pcoa.var.perN[2], "%","]" ,sep=" ")) + 
   geom_vline(xintercept = 0, linetype = "dashed") + 
   geom_hline(yintercept = 0, linetype = "dashed") +
  # geom_segment(data=vec.sp.df_F.sig, 
  #              aes(x=0,xend=Dim1,y=0,yend=Dim2),
  #              arrow = arrow(length = unit(0.3, "cm")),
  #              colour="red", size = 1,
  #              inherit.aes=FALSE) + 
  # geom_text(data=vec.sp.df_F.sig,
  #           aes(x=Dim1,y=Dim2,label=species),size=4,
  #           inherit.aes=FALSE) + 
  scale_shape_manual(values=c(15:17)) +
  ordplot_theme + theme(legend.box = "vertical") + 
  guides(shape = guide_legend(order = 1)) +
  scale_color_gradient(low = "blue", high = "red", name="*D. hansenii* abundance",
                       labels=c("Low","High"),breaks=c(200,1300), guide = "colourbar") +
  #   ylim(-0.5, 0.75) +
  # xlim(-0.58, 0.96) +
  ggtitle("Litter samples by ASV1 *D. hansenii* abundance")

taxa.n.deb
```

```{r fig.height = 10, fig.width = 18, dpi=300}
taxa.n.days <- ggplot(data=pcoa.dataN, aes(x = X, y = Y, colour = Age)) +
  geom_point(size=7, aes(shape=Aspergillosis)) +
  xlab(paste("PCoA 1","[" ,pcoa.var.perN[1], "%","]" ,sep=" ")) +
  ylab(paste("PCoA 2","[" ,pcoa.var.perN[2], "%","]" ,sep=" ")) + 
  geom_vline(xintercept = 0, linetype = "dashed") + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  # geom_segment(data=vec.sp.df_N.sig, 
  #              aes(x=0,xend=Dim1,y=0,yend=Dim2),
  #              arrow = arrow(length = unit(0.3, "cm")),
  #              colour="red", size = 1,
  #              inherit.aes=FALSE) + 
  # geom_text(data=vec.sp.df_N.sig,
  #           aes(x=Dim1,y=Dim2,label=species),size=4,
  #           inherit.aes=FALSE) + 
  scale_color_manual(values = c("#788374","#ebd27d","#aa644d","#372a39")) + 
  scale_shape_manual(values=c(15:17)) +
  ordplot_theme + theme(legend.box = "vertical") + 
  guides(color = guide_legend(nrow = 2), shape = guide_legend(order = 1)) +
  #   ylim(-0.65, 0.9) +
  # xlim(-0.75, 0.9) +
  ggtitle("Litter samples by days since first chick")


taxa.n.days
```

```{r fig.height = 10, fig.width = 18, dpi=300}
taxa.n.vec <- ggplot(data=pcoa.dataN, aes(x = X, y = Y)) +
  xlab(paste("PCoA 1","[" ,pcoa.var.perN[1], "%","]" ,sep=" ")) +
  ylab(paste("PCoA 2","[" ,pcoa.var.perN[2], "%","]" ,sep=" ")) + 
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_segment(data=vec.sp.df_N.sig,
               aes(x=0,xend=Dim1,y=0,yend=Dim2),
               arrow = arrow(length = unit(0.3, "cm")),
               colour="red", size = 1,
               inherit.aes=FALSE) +
  geom_text_repel(data=vec.sp.df_N.sig,
            aes(x=Dim1,y=Dim2,label=species),size=7.5,
            inherit.aes=FALSE) +
 ordplot_theme + #theme(legend.box = "vertical") + 
       ylim(-0.6, 0.9) +
       xlim(-0.87, 1.05) +
  ggtitle("Influential ASV vectors for ordinated litter samples")

taxa.n.vec
```

```{r fig.cap = "K\u101k\u101p\u14d PCoA plot with taxonomic vectors",fig.height = 10, fig.width = 18, dpi=300}
taxa.n.nest <- ggplot(data=pcoa.dataN, aes(x = X, y = Y, colour = Nest)) +
  geom_point(size=5, aes(shape=Aspergillosis)) +
  xlab(paste("PCoA 1","[" ,pcoa.var.perN[1], "%","]" ,sep=" ")) +
  ylab(paste("PCoA 2","[" ,pcoa.var.perN[2], "%","]" ,sep=" ")) + 
  geom_vline(xintercept = 0, linetype = "dashed") + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_segment(data=vec.sp.df_N.sig, 
               aes(x=0,xend=Dim1,y=0,yend=Dim2),
               arrow = arrow(length = unit(0.3, "cm")),
               colour="red", size = 1,
               inherit.aes=FALSE) + 
  geom_text(data=vec.sp.df_N.sig,
            aes(x=Dim1,y=Dim2,label=species),size=4,
            inherit.aes=FALSE) + 
  scale_color_manual(values = nest.f.col.litter) + 
  scale_shape_manual(values=c(15:17)) +
  ordplot_theme + theme(legend.box = "vertical") + 
  guides(color = guide_legend(order = 1)) +
    ylim(-0.65, 0.9) +
  xlim(-0.75, 0.9) +
  ggtitle("Litter samples by nest")


taxa.n.nest
```

```{r fig.height = 20, fig.width = 36, dpi=300}
pcoa_litter_ords <-  ggarrange(taxa.n.loc, taxa.n.deb, taxa.n.days, taxa.n.vec, labels = c("A","B","C","D"), ncol = 2, nrow=2, font.label = list(size = 30))
pcoa_litter_ords
ggsave("FINAL/ordinations/taxa_vectors_litter_edit_SEPT.png", pcoa_litter_ords, width = 36, height = 20, dpi = 400, bg = "white")
```


#Mixed models

```{r}
library(lme4); packageVersion("lme4")

glom_f_genus <- tax_glom(psF_RA, taxrank = 'Genus')

tax.table.g <- data.frame(otu_table(glom_f_genus))
tax.glom.g <- data.frame(tax_table(glom_f_genus))
tax.map.g <- data.frame(sample_data(glom_f_genus))

names(tax.table.g) <- tax.glom.g$Genus

taxa.model.map.g <- cbind(tax.map.g,tax.table.g)

#Kazachstania
kaz.model <- lme4::lmer(Kazachstania ~ Age + (1|Name), data=taxa.model.map.g)
summary(kaz.model)
null.kaz.model <- lme4::lmer(Kazachstania ~ (1|Name), data=taxa.model.map.g)
anova(null.kaz.model,kaz.model)

kaz.model.asp <- lme4::lmer(Kazachstania ~ Aspergillosis + (1|Name), data=taxa.model.map.g)
summary(kaz.model.asp)
anova(null.kaz.model,kaz.model.asp)

kaz.model.L <- lme4::lmer(Kazachstania ~ Island + (1|Name), data=taxa.model.map.g)
summary(kaz.model.L)
anova(null.kaz.model,kaz.model.L)

#Debaryomyces
deb.model <- lme4::lmer(Debaryomyces ~ Age + (1|Name), data=taxa.model.map.g)
summary(deb.model)
null.deb.model <- lme4::lmer(Debaryomyces ~ (1|Name), data=taxa.model.map.g)
anova(null.deb.model,deb.model)

deb.model.asp <- lme4::lmer(Debaryomyces ~ Aspergillosis + (1|Name), data=taxa.model.map.g)
summary(deb.model.asp)
anova(null.deb.model,deb.model.asp)

deb.model.L <- lme4::lmer(Debaryomyces ~ Island + (1|Name), data=taxa.model.map.g)
summary(deb.model.L)
anova(null.deb.model,deb.model.L)

#Apiotrichum
apio.model <- lme4::lmer(Apiotrichum ~ Age + (1|Name), data=taxa.model.map.g)
summary(apio.model)
null.apio.model <- lme4::lmer(Apiotrichum ~ (1|Name), data=taxa.model.map.g)
anova(null.apio.model,apio.model)

apio.model.asp <- lme4::lmer(Apiotrichum ~ Aspergillosis + (1|Name), data=taxa.model.map.g)
summary(apio.model.asp)
anova(null.apio.model,apio.model.asp)

apio.model.L <- lme4::lmer(Apiotrichum ~ Island + (1|Name), data=taxa.model.map.g)
summary(apio.model.L)
anova(null.apio.model,apio.model.L)

#Candida
candida.model <- lme4::lmer(Candida ~ Age + (1|Name), data=taxa.model.map.g)
summary(candida.model)
null.candida.model <- lme4::lmer(Candida ~ (1|Name), data=taxa.model.map.g)
anova(null.candida.model,candida.model)

candida.model..asp <- lme4::lmer(Candida ~ Aspergillosis + (1|Name), data=taxa.model.map.g)
summary(candida.model..asp)
anova(null.candida.model,candida.model..asp)

candida.model.L <- lme4::lmer(Candida ~ Island + (1|Name), data=taxa.model.map.g)
summary(candida.model.L)
anova(null.candida.model,candida.model.L)
```

```{r}
mm.p.adj <- c("0.007","0.004","0.009","0.002")
p.adjust(mm.p.adj, method = "BH")
```

